### 2016-09-16 Slides/morality-slides.Rmd
First commit.

---
title: "The Morality of Arbitrage"
author: "Tyler J. Brough"
date: "September 16, 2016"
output: pdf_document
---

#

> But nobody can be a great economist who is only an economist - and I am even tempted to add that the economist who
> is only an economist is likely to become a nuisance if not a positive danger.

-- Friedrich von Hayek

### 2016-09-16 Slides/render.R

@@ -1,0 +1,3 @@
+library(rmarkdown)
+rmarkdown::render("morality-slides.Rmd")
+

### 2016-09-16 Slides/morality-slides.Rmd
Progress on slides.

@@
 date: "September 16, 2016"
-output: pdf_document
+output: ioslides_presentation
 ---
@@
 
-> But nobody can be a great economist who is only an economist - and I am even tempted to add that the economist who
-> is only an economist is likely to become a nuisance if not a positive danger.
+> *But nobody can be a great economist who is only an economist - and I am even tempted to add that the economist who is only an economist is likely to become a nuisance if not a positive danger*.
 
 -- Friedrich von Hayek
+
+## Introduction
+
+>- I have been very influenced by Coases's 1975 AER article *The Market for Goods and the Market for Ideas*.
+>- I have also been reading articles lately by Robert Nau and his coauthors. In particular the paper by Nau & McCardle (1991) *Aribtrage, Rationality, and Equilibrium*. 
+>- This project is an attempt to do something like what Coase had in mind, using the the approach of Nau, but applied to the morality of markets and capitalism.
+
+## Nau's Arbitrage Choice Theory

### 2016-09-23 Slides/morality-slides.Rmd
Updated title to hint at informality.
Finished slides.

@@
 ---
-title: "The Morality of Arbitrage"
+title: "The Morality of Arbitrage - Some Half-Baked Ideas"
 author: "Tyler J. Brough"
@@
 
+<div class="notes">
+- Of course, all good ideas begin with Hayek!
+</div>
+
+## What's Wrong with Capitalism?!
+
+>- It is apparent to me that the standard ethical arguments for capitalism are not having any purchase in the minds of most people.
+>- Capitalism is presented as some kind of Faustian bargain: we like it for its wealth production and efficiency, but at bottom it is really about greed. It is rapacious and immoral.
+>- It is readily apparent that many of our colleagues in the business disciplines believe this notion
+>- __I'm afraid that our students do too!__ They leave here with some good technical tools, but not with an appreciation of just how much good they will do in their careers. 
+>- That is on us! That's a failure on our part to teach correct principles.
+
+## Some Evidence
+
+I asked my finance bros (and sis) for examples of the "evils" of finance and capitalism:
+
+From Paul:
+
+>- The Rolling Stone writes about the [great vampire squid wrapped around the face of humanity](http://www.rollingstone.com/politics/news/the-great-american-bubble-machine-20100405)
+
+From Ben:
+
+>- "Derivatives are financial weapons of mass destruction" - Warren Buffett
+>- "Derivatives are toxic - stay away from them" - unnamed donor to the Huntsman School
+>- "In a world where profit is consistently put before both people and the planet, climate economics has everything to do with ethics and morality" - Naomi Klein
+
+## Some Evidence Continued
+
+From Ryan:
+
+>- "I heard a quote on the radio today that 46% of millenials don't think capitalism works."
+>- "The Occupy Wall Street protests are shining a national spotlight on the most powerful, dangerous and secretive economic and political force in America." --Bernie Sanders
+>- "What Wall Street and credit card companies are doing is really not much different from what gangsters and loan sharks do who make predatory loans.
+While the bankers wear three-piece suits and don't break the knee caps of those who can't pay back, they still are destroying people's lives." --Bernie Sanders
+
+## Yet More Evidence
+
+From Dani:
+
+>-  JF from 2015 by Zingales is [*Does Finance Benefit Society?*](http://faculty.chicagobooth.edu/luigi.zingales/papers/research/finance.pdf)
+
+Some more:
+
+>- CNN asks: [Is democratic socialism the right path for America?](http://www.cnn.com/2015/10/27/opinions/opinion-roundup-socialism/)
+
 ## Introduction
 
->- I have been very influenced by Coases's 1975 AER article *The Market for Goods and the Market for Ideas*.
->- I have also been reading articles lately by Robert Nau and his coauthors. In particular the paper by Nau & McCardle (1991) *Aribtrage, Rationality, and Equilibrium*. 
->- This project is an attempt to do something like what Coase had in mind, using the the approach of Nau, but applied to the morality of markets and capitalism.
+The origins of this project have been slowly baking for some time now:
+
+- I have been very influenced by coase's 1974 AER article [*The Market for Goods and the Market for Ideas*](http://www.jstor.org/stable/1816070?seq=1#page_scan_tab_contents).
+
+## Coase's Dutch Book Argument
+
+Coase's paper is about what he calls the "economics of the First Ammendment"
+
+For those needing a refresher:
+
+> _"Congress shall make no law respecting an establishment of religion, or prohibiting the free exercise thereof; or abridging the freedom of speech, or of the press; or the right of the people peaceably to assemble, and to petition the Government for a redress of grievances"_
+
+<div class="notes">
+
+If you don't know what a Dutch book is, hang on and I'll explain it.
+</div>
+
+## Coase's Dutch Book Continued
+
+The main idea that he examines:
+
+> _"What is the general view that I will be examining?
+It is that, in the market for goods, government regulation is desirable whereas, in the market for ideas, government regulation is undersirable and should be strictly limited."_
+
+The Dutch book is as follows:
+
+> _"The paradox is that government intervention which is so harmful in the one sphere becomes beneficial in the other."_
+
+and
+
+> _"...
+it is usually those who press most strongly for an extension of government regulation in other markets who are most anxious for a vigorous enforcement of the First Amendment prohibitions on government regulation in the market for ideas"_
+
+## Coase Continued
+
+Coase's take:
+
+> _"Because of the view that a free market in ideas is necessary to the maintenance of democratic institutions and , I believe, for other reasons also, intellectuals have shown a tendency to exalt the market for ideas and to depreciate the market for goods._ ___Such an attitude seems to me unjustified.___"
+
+> _"I would put the point more bluntly.
+The market for ideas is the market in which the intellectual conducts his trade.
+The explanation of the paradox is self-interest and self-esteem.
+Self-esteem leads the intellectuals to magnify the importance of their own market.
+That others should be regulated seems naturally, particularly as many of the intellectuals see themselves as doing the regulating.
+But self-interest combines with self-esteem to ensure that, while others are regulated, regulation should not apply to them."_
+
+## Yet more Coase
+
+> _"It is hard to believe that the general public is in a better position to evaluate competing views on economic and social policy than to choose between different kinds of food."_
+
+> _"I do not believe that we will be able to form a judgement in which we can have any confidence unless we abandon the present ambivalence about the performance of government in the two markets and adopt a more consistent view"_
+
+>- One might say a more "___coherent___" view
+
+## Buchanan & Hayek Discussion
+
+<iframe width="1280" height="720" src="https://www.youtube.com/embed/kzNpD9DXU2w" frameborder="0" allowfullscreen></iframe>
+
+<div class="notes">
+Go to 1:39 in the video.
+</div>
 
 ## Nau's Arbitrage Choice Theory
+
+Some time ago I came across Robert Nau's work on [*Arbitrage Choice Theory*](https://faculty.fuqua.duke.edu/~rnau/bio/)
+
+```{r, echo=FALSE, out.width = "300px", out.height="400px"}
+knitr::include_graphics("images/Nau.jpg")
+```
+
+## Bruno de Finetti
+
+To understand Nau, we need to first understand [Bruno de Finetti](https://en.wikipedia.org/wiki/Bruno_de_Finetti)
+
+```{r, echo=FALSE, out.width = "300px", out.height="400px"}
+knitr::include_graphics("images/deFinetti.jpg")
+```
+
+## de Finetti and Dutch Books
+
+de Finetti had a very operational view of subjective Bayesian probability.
+
+Nau on de Finetti:
+
+> _"In de Finetti's theory, bets are for money, so your probability of an event is effectively the price that you are willing to pay for a lottery ticket that yields 1 unit of money if the event occurs and nothing otherwise."_
+
+>- My finance colleagues will understand de Finetti's lottery tickets as contingent claims.
+>- In fact, de Finetti already invented much of what we thing of as modern finance.
+[But no one really knew about it!](https://www.openstarts.units.it/dspace/bitstream/10077/3969/1/Pressacco%20Ziani%20Atti%20Economia%20e%20Incertezza.pdf)
+
+## Dutch Book Arguments
+
+According to *The Cambridge Dictionary of Philosophy* at Dutch book argument is the following:
+
+> ___The argument that a rational person's degrees of belief must conform to the axioms of the probability calculus, since otherwise, by the Dutch book theorem, he would be vulnerable to a Dutch book.___
+
+Okay, so what is the Dutch Book Theorem?
+
+> ___The proposition that anyone who (a) counts a bet on a proposition p as fair if the odds correspond to his degree of belief that p is true and who (b) is willing to make any combination of bets he would regard individually as fair will be vulnerable to a Dutch book provided his degrees of belief do not conform to the axioms of the probability calculus.
+Thus, anyone of whom (a) and (b) are true and whose degree of belief in a disjunction of two incompatible propositions is not equal to the sum of his degrees of belief in the two propositions taken individually would be vulnerable to a Dutch book.___
+
+## Here's An Easier Version
+
+From the great comic strip [xkcd](https://xkcd.com/1132/)
+
+```{r, echo=FALSE, out.width = "600px", out.height="450px"}
+knitr::include_graphics("images/xkcd.png")
+```
+
+## Back to Nau
+
+From Nau's excellent paper [__Arbitrage, Rationality, and Equilibirum__](http://link.springer.com/article/10.1007/BF00132993):
+
+> _"In this paper it will be argued that decision theory, game theory, and market theory can be placed on a more secure and parsimonious footing by appeal to the principle of_ ___no arbitrage___ _rather than the usual ordering axioms of preferences.
+The arbitrage princile already has a long history: in the literature on Bayesian statistics and decision theory, it was introduced by de Finetti (1937) as a basis for defining subjective probability...
+In the finance literature, the arbitrage principle explicitly underlies the capital structure theorem (Modigliani & Miller 1958), the valuation of cash flows (Ross 1978), and the pricing of assets and options (Black and Scholes 1973, Merton 1973, Ross 1976).
+No-arbitrage is central to classical welfare economics, where it goes by the name of 'Pareto optimality.'_
+
+## More Nau
+
+> _"It will be shown here that no-arbitrage is the core principle of rationality which remains after economic models are stripped of their excess baggage of intrinsically unverifiable or empirically disconfirmed assumptions about the perfectness of human cognition, particularly the assumption that belief and preference orderings are complete.
+The arbitrage principle still provides support for the most important concepts of equilibrium in games and markets, but with weaker information requirements.
+It is consistent with 'procedural' or 'cognitive' views of rationality (e.g., Simon 1976; Munier 1991) which emphasize that the information-processing capabilities of the individual are finite and tailored to the specific demands of her physical and cultural environment."_
+
+And my favorite line:
+
+> _"Thus, Bayesians are made, not born."_
+
+## Thoughts on Nau
+
+>- So the Dutch book, or equivalently the no-arbitrage principle becomes a unifying theme. 
+>- We can now explicitly make Coase's argument as a Dutch book argument and point out the incoherence
+
+<div class="notes">
+Some subtle points:
+
+- Nau points out that probabilities and utilities are inseparable, so we must interpret them as risk-neutral probabilities
+- We in finance are very comfortable with that!
+
+There is much deep material here. So much to be done in following up!
+</div>
+
+## From Nau back to Hayek
+
+The foundational paper in economics, is for me, Hayek's 1945 AER [The Use of Knowledge in Society](http://www.econlib.org/library/Essays/hykKnw1.html)
+
+>- Hayek points out that market processes are knowledge processes. 
+>- It should seem very natural to economists to treat the market for ideas and the market for goods similarly. The are about the same thing!
+>- Thus, the process of scholarship and science are very much like market process for goods.
+
+Additionally,
+
+>- A successful research project is an intellectual arbitrage.
+>- Students come into our class rooms every day with open Dutch books and pay us to exploit them!
+>- Every technological advance, life-improving result of human ingenuity is entrepreneurial arbitrage!
+
+## Thomas Sowell on Hayek
+
+```{r, echo=FALSE, out.width = "600px", out.height="450px"}
+knitr::include_graphics("images/thomas-sowell.jpg")
+```
+
+## Thomas Sowell Quotation
+
+> ___"While market economies are often thought of as money economies, they are still more so knowledge economies... Economic transactions are purchases and sales of knowledge."___
+
+> ___"After all, the caveman had the same natural resources at their disposal as we have today...
+We are all in the business of buying and selling knowledge from one another, because we are each so profoundly ignorant of what it takes to complete the whole process of which we are a part."___
+
+## The Morality of Scholarship and the Morality of Arbitrage
+
+>- The process of scholarship is generally accepted as an inherently moral pursuit!
+>- Scholarship and science are about important ideas and beliefs
+>- Economics and finance are about more mundane information processes, but certainly no less vital. Probably much more important to our daily lives!
+
+## Brough's Dutch Book Argument
+
+One cannot simultaneously believe that:
+
+1. The pursuit of knowledge (_intellectual arbitrage_) is inherently moral
+
+and that
+
+2. The pursuit of capitalist enterprise (_entrepreneurial arbitrage_) is inherently immoral
+
+without leaving yourself open to a massive Dutch book, for they are just two different examples of the very same thing!
+
+## Notes
+
+>- I am a bit embarrased to admit that until very recently I was not aware of Israel Kirzner's very important work on entrepreneurial arbitrage.
+>- Dutch books in the election cycle? Like Thomas Sowell once said, "I feel like a mosquito at a nudist collony. Where do I begin?!"
+>- Ben thinks that one of the problems is the lack of arbiragable positions. 
+>- We all have the same vote, so there is no one person who can really move the market with superior knowledge. What we get is mass confusion!

### 2016-09-23 Slides/morality-slides.Rmd
Fixed a few errors.

@@
 author: "Tyler J. Brough"
-date: "September 16, 2016"
+date: "September 23, 2016"
 output: ioslides_presentation
@@
 
+The freedom of speech, a free press, religious liberty are so ingrained in our culture. Their morality is based on a generally held and accepted ethical foundation.
+
 <div class="notes">
@@
 Self-esteem leads the intellectuals to magnify the importance of their own market.
-That others should be regulated seems naturally, particularly as many of the intellectuals see themselves as doing the regulating.
+That others should be regulated seems natural, particularly as many of the intellectuals see themselves as doing the regulating.
 But self-interest combines with self-esteem to ensure that, while others are regulated, regulation should not apply to them."_
@@
 
-> _"I do not believe that we will be able to form a judgement in which we can have any confidence unless we abandon the present ambivalence about the performance of government in the two markets and adopt a more consistent view"_
+> _"I do not believe that we will be able to form a judgement in which we can have any confidence unless we abandon the present ambivalence about the performance of government in the two markets and adopt a more consistent view."_
 
@@
 >- My finance colleagues will understand de Finetti's lottery tickets as contingent claims.
->- In fact, de Finetti already invented much of what we thing of as modern finance.
+>- In fact, de Finetti already invented much of what we think of as modern finance.
 [But no one really knew about it!](https://www.openstarts.units.it/dspace/bitstream/10077/3969/1/Pressacco%20Ziani%20Atti%20Economia%20e%20Incertezza.pdf)
@@
 
-According to *The Cambridge Dictionary of Philosophy* at Dutch book argument is the following:
+According to *The Cambridge Dictionary of Philosophy* a Dutch book argument is the following:
 
@@
 
-## Here's An Easier Version
+## xkcd On Dutch Books
 
-From the great comic strip [xkcd](https://xkcd.com/1132/)
-
-```{r, echo=FALSE, out.width = "600px", out.height="450px"}
+```{r, echo=FALSE, out.width = "600px", out.height="490px"}
 knitr::include_graphics("images/xkcd.png")
 ```
+
+Here is the [link.](https://xkcd.com/1132/)
 
@@
 In the finance literature, the arbitrage principle explicitly underlies the capital structure theorem (Modigliani & Miller 1958), the valuation of cash flows (Ross 1978), and the pricing of assets and options (Black and Scholes 1973, Merton 1973, Ross 1976).
-No-arbitrage is central to classical welfare economics, where it goes by the name of 'Pareto optimality.'_
+No-arbitrage is central to classical welfare economics, where it goes by the name of 'Pareto optimality.'"_
 
@@
 
->- So the Dutch book, or equivalently the no-arbitrage principle becomes a unifying theme. 
->- We can now explicitly make Coase's argument as a Dutch book argument and point out the incoherence
+>- So the Dutch book, or equivalently the no-arbitrage principle, becomes a unifying theme. 
+>- We can now explicitly make Coase's argument as a Dutch book argument and point out the incoherence.
 
@@
 >- Hayek points out that market processes are knowledge processes. 
->- It should seem very natural to economists to treat the market for ideas and the market for goods similarly. The are about the same thing!
->- Thus, the process of scholarship and science are very much like market process for goods.
+>- It should seem very natural to economists to treat the market for ideas and the market for goods similarly. They are two different markets, but the same market process!
+>- Thus, the process of scholarship and science are very much like the market process for goods.
 
-Additionally,
+Additionally
 
@@
 
-## Thomas Sowell Quotation
+## Thomas Sowell Quotations
 
@@
 >- The process of scholarship is generally accepted as an inherently moral pursuit!
->- Scholarship and science are about important ideas and beliefs
+>- Scholarship, science, and journalism are about important ideas and beliefs.
 >- Economics and finance are about more mundane information processes, but certainly no less vital. Probably much more important to our daily lives!
@@
 
-1. The pursuit of knowledge (_intellectual arbitrage_) is inherently moral
+  $(1)$ The pursuit of knowledge (_intellectual arbitrage_) is inherently moral
 
@@
 
-2. The pursuit of capitalist enterprise (_entrepreneurial arbitrage_) is inherently immoral
+  $(2)$ The pursuit of capitalist enterprise (_entrepreneurial arbitrage_) is inherently immoral
 
-without leaving yourself open to a massive Dutch book, for they are just two different examples of the very same thing!
+without leaving oneself open to a massive Dutch book. They are just two different examples of the very same thing!
 
@@
 >- Dutch books in the election cycle? Like Thomas Sowell once said, "I feel like a mosquito at a nudist collony. Where do I begin?!"
->- Ben thinks that one of the problems is the lack of arbiragable positions. 
+>- Ben thinks that one of the problems is the lack of arbitragable positions. 
 >- We all have the same vote, so there is no one person who can really move the market with superior knowledge. What we get is mass confusion! 
+>- Once you start seeing the world this way you will see Dutch books everywhere. Especially on Facebook.

### 2016-09-23 Slides/render.R
Creating project page.

@@ -1,3 +1,0 @@
-library(rmarkdown)
-rmarkdown::render("morality-slides.Rmd")
-

### 2016-11-30 APEE/morality-of-arbitrage-abstract.Rmd
Adding the APEE abstract write up.

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ./svm-latex-ms.tex
title: "The Morality of Arbitrage"
author:
- name: Tyler J. Brough
  affiliation: Utah State University
abstract: "In this paper, I argue that one cannot rationally believe that financial arbitrage is an inherently immoral pursuit, while simultaneously believing that the pursuit of academic knowledge is an inherently moral pursuit. I argue that these two seemingly separate activities are really one and the same. Further those that do hold such contradictory beliefs are behaving incoherently and have a Dutch book made against them."
keywords: "arbitrage, Dutch books, morality"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
# spacing: double
bibliography: ./master.bib
biblio-style: apsr
---

# Introduction

The pursuit of knowledge through academic scholarship rests on a commonly held moral foundation. The pursuit of truth, which is widely believed to be the goal of scholarship, is thought to be an inherently moral activity. At the same time, it is an increasingly widely held belief that financial market arbitrage, the kind pursued by Wall Street traders, is an inherently immoral activity. Take for example, the case of the quantitative proprietary trading firm which serves no clients and which invests only the capital of its principals. Such a firm makes its profits, often astonishingly large profits, by buying and selling financial securities and profiting from speculation. A common line is of reasoning is that such a firm is predatory, parasitic, and even rapacious and as such cannot possibly be acting morally.

In this paper, I argue that one cannot simultaneously hold the above two positions without behaving incoherently. The process of scholarship and financial trading are both examples of finding and exploiting Dutch books. Dutch books are simply arbitrage by another name. Thus scholarship can be seen, indeed is most properly seen, as a form of intellectual arbitrage. Just as traders find mispricings in financial securities and exploit them for financial profit, scholars find misunderstandings - mispricings by another name - and exploit them to establish their scholarly reputation.

@Coase1974, in what he referred to as the economics of the First Amendment, makes a similar argument by comparing the "market for ideas" and the more mundane "market for goods." In his analysis he points out a broad inconsistency in the way these two different markets are viewed: that the market for goods is inefficient and requires government regulation to tame it, but that it would even be immoral for government to seek to regulate the market for ideas. Coase points out that this view is fundamentally inconsistent:

> _Consider the question of consumer ignorance which is commonly thought to be a justification for government intervention. It is hard to believe that the general public is in a better position to evaluate competing views on economic and social policy than to choose between different kinds of food._

Coase states further:

> _Because of the view that a free market in ideas is necessary to the maintenance of democratic institutions and, I believe, for other reasons also, intellectuals have shown a tendency to exalt the market for ideas and to depreciate the market for goods. Such an attitude seems to me unjustified._

I argue, that not only is such a view unjustified but it is irredeemably incoherent and irrational. In pointing out the tendency of intellectuals to favor the market for ideas over the market for goods, Coase was echoing @Hayek1945, who wrote of "the relative importance of the different kinds of knowledge" and the fact that "one kind of knowledge, namely, scientific knowledge, occupies now so prominent a place in public imagination that we tend to forget that it is not the only kind that is relevant." Indeed, by taking advantage of relative mispricings among commodities the financial trader benefits his fellow men by allocating resources more efficiently. But this is hardly viewed as a noble act, not nearly so noble as scientific discovery or academic expression. Hayek saw keenly the situation:

> _It is a curious fact that this sort of knowledge should today be generally regarded with a kind of contempt, and that someone who by such knowledge gains an advantage over somebody better equipped with theoretical or technical knowledge is thought to have acted almost disreputably. To gain advantage from better knowledge of facilities of communication or transport is sometimes regarded as almost dishonest, although it is quite as important that society make use of the best opportunities in this respect as in using the latest scientific discoveries._

The lesson regarding the relative importance of different kinds of knowledge that Hayek teaches is a very deep one. Indeed, when this insight is fully appreciated one begins to see that the use of mundane kinds of knowledge - Hayek's "knowledge of time and place" is essential. It is not exaggeration to state that if the only knowledge that society could usefully exploit was that from universities, the press, literature and science we would all starve to death in very short order. The financial arbitrageur is a perfect example of Hayek's "man on the spot" and his actions benefit his fellows greatly. Still, when one thinks of the abstract concept of the pursuit of knowledge, images of the scientist in the lab or of the poet in the library come more easily to mind than the trader scanning prices on his bank of monitors. But for Hayek:

> _the arbitrageur who gains from local differences of commodity prices, [is] performing [an] eminently useful function based on special knowledge of circumstances of the fleeting moment not known to others._

The actions of the arbitrageur are indeed eminently useful! Consider the commodities that we require in our daily lives such as sugar, coffee, wheat, milk, and oil that come to us more efficiently and at lower cost than would otherwise be the case if not for the actions of commodity traders. In addition, because of financial traders retirement is secured more soundly through investment. And risks are insured against, eliminated and transferred through financial markets that we would otherwise have to bear.

Hayek compared the price system to "a kind of machinery for registering change" and as a "system of telecommunications." Similarly, @Scarf1990 has made an analogy between the market institution and a massively distributed analog computer that computes values in the form of prices. Following this line of reasoning, all market processes are knowledge processes. Therefore there is not sharp distinction between the "market for ideas" and the "market for goods", as Coase referred to them. They are simply both markets and differ only in their relative kinds of knowledge. @Sowell1996 has made this point quite succinctly:

> _While market economies are often thought of as money economies, they are still more so knowledge economies... Economic transactions are purchases and sales of knowledge._

> _After all, the cavemen had the same natural resources at their disposal as we have today... We are all in the business of buying and selling knowledge from one another, because we are each so profoundly ignorant of what it takes to complete the whole process of which we are part._

The link between the market for ideas and the market for goods is further strengthened by considering the work of the decision theorist Robert Nau. For example, @NauMcCardle1991 state that the principle of no-arbitrage, which is fundamental in finance theory, is the common foundation of decision theory, game theory and competitive market theory. @Nau1999 refers to this as Arbitrage Choice Theory, following the Bayesian Dutch book arguments of @deFinetti1937. A Dutch book is a situation in which an individual holds incoherent beliefs (beliefs inconsistent with the basic axioms of probability), and if forced to bet on them exposes themself to a guaranteed loss. When market transactions are seen as knowledge transactions, it becomes clear that a Dutch book is equivalent to arbitrage - the good old fashioned kind often derided from the world of finance. This leads to the Dutch book theorem, which the Cambridge Dictionary of Philosophy (1999) defines as:

> The proposition that anyone who (a) counts a bet on a proposition p as fair if the odds correspond to his degree of belief that p is true and who (b) is willing to make any combination of bets he would regard individually as fair will be vulnerable to a Dutch book provided his degrees of belief do not conform tot he axioms of the probability calculus. Thus, anyone of whom (a) and (b) are true and whos degree of belief in a disjuntion of two incompatible propositions is not equal to the sum of his degrees of belief in the two propositions taken individually would be vulnerable to a Dutch book.

When a trader makes a profit by simultaneously buying and selling financial securities to exploit relative mispricings, this arbitrage is simply the exploitation of a Dutch book expressed as incoherent market prices. Likewise the intellectual pursuit of knowledge, what Coase called the "market for ideas" can be seen as the pursuit of arbitrage, or Dutch books, in the existing body of academic knowledge. Consider a young scholar who discovers an error in the received theory of their specific academic domain, and who makes a name for themself by publishing an article correcting the error in a reputable academic journal. This can now be easily understood to be the exploitation of a Dutch book, or intellectual arbitrage.

My argument can now be stated simply as follows. One cannot simultaneously believe: (a) that the pursuit of academic or scientific knowledge is inherently moral, and (b) that the pursuit of capitalist profits through financial arbitrage is inherently immoral.

There is thus a logical defeator for the belief that arbitrage is immoral. Financial arbitrage rests on the same moral foundation as scholarship - the pursuit of knowledge - albeit in a more plain and mundate way.

<!--
# References
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\vspace*{-0.2in}
\noindent
-->

### 2016-11-30 APEE/morality-of-arbitrage-abstract.tex
Adding the APEE abstract write up.

\documentclass[11pt,]{article}
\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}

  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}

\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center

\renewenvironment{abstract}
 {{%
    \setlength{\leftmargin}{0mm}
    \setlength{\rightmargin}{\leftmargin}%
  }%
  \relax}
 {\endlist}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother

\setcounter{secnumdepth}{0}

\title{The Morality of Arbitrage  }

\author{\Large Tyler J. Brough\vspace{0.05in} \newline\normalsize\emph{Utah State University}  }

\date{}

\usepackage{titlesec}

\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\itshape}
\titleformat*{\subsubsection}{\normalsize\itshape}
\titleformat*{\paragraph}{\normalsize\itshape}
\titleformat*{\subparagraph}{\normalsize\itshape}

\usepackage{natbib}
\bibliographystyle{apsr}

\newtheorem{hypothesis}{Hypothesis}
\usepackage{setspace}

\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Tyler J. Brough (Utah State University)},
             pdfkeywords = {arbitrage, Dutch books, morality},  
            pdftitle={The Morality of Arbitrage},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}

% \pagenumbering{arabic}% resets `page` counter to 1 
%
% \maketitle

{% \usefont{T1}{pnc}{m}{n}
\setlength{\parindent}{0pt}
\thispagestyle{plain}
{\fontsize{18}{20}\selectfont\raggedright 
\maketitle  % title \par

}

{
   \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
\textbf{\authorfont Tyler J. Brough} \hskip 15pt \emph{\small Utah State University}

}

}

\begin{abstract}

    \hbox{\vrule height .2pt width 39.14pc}

    \vskip 8.5pt % \small

\noindent In this paper, I argue that one cannot rationally believe that financial
arbitrage is an inherently immoral pursuit, while simultaneously
believing that the pursuit of academic knowledge is an inherently moral
pursuit. I argue that these two seemingly separate activities are really
one and the same. Further those that do hold such contradictory beliefs
are behaving incoherently and have a Dutch book made against them.

\vskip 8.5pt \noindent \emph{Keywords}: arbitrage, Dutch books, morality \par

    \hbox{\vrule height .2pt width 39.14pc}

\end{abstract}

\vskip 6.5pt

\noindent  \section{Introduction}\label{introduction}

The pursuit of knowledge through academic scholarship rests on a
commonly held moral foundation. The pursuit of truth, which is widely
believed to be the goal of scholarship, is thought to be an inherently
moral activity. At the same time, it is an increasingly widely held
belief that financial market arbitrage, the kind pursued by Wall Street
traders, is an inherently immoral activity. Take for example, the case
of the quantitative proprietary trading firm which serves no clients and
which invests only the capital of its principals. Such a firm makes its
profits, often astonishingly large profits, by buying and selling
financial securities and profiting from speculation. A common line is of
reasoning is that such a firm is predatory, parasitic, and even
rapacious and as such cannot possibly be acting morally.

In this paper, I argue that one cannot simultaneously hold the above two
positions without behaving incoherently. The process of scholarship and
financial trading are both examples of finding and exploiting Dutch
books. Dutch books are simply arbitrage by another name. Thus
scholarship can be seen, indeed is most properly seen, as a form of
intellectual arbitrage. Just as traders find mispricings in financial
securities and exploit them for financial profit, scholars find
misunderstandings - mispricings by another name - and exploit them to
establish their scholarly reputation.

\citet{Coase1974}, in what he referred to as the economics of the First
Amendment, makes a similar argument by comparing the ``market for
ideas'' and the more mundane ``market for goods.'' In his analysis he
points out a broad inconsistency in the way these two different markets
are viewed: that the market for goods is inefficient and requires
government regulation to tame it, but that it would even be immoral for
government to seek to regulate the market for ideas. Coase points out
that this view is fundamentally inconsistent:

\begin{quote}
\emph{Consider the question of consumer ignorance which is commonly
thought to be a justification for government intervention. It is hard to
believe that the general public is in a better position to evaluate
competing views on economic and social policy than to choose between
different kinds of food.}
\end{quote}

Coase states further:

\begin{quote}
\emph{Because of the view that a free market in ideas is necessary to
the maintenance of democratic institutions and, I believe, for other
reasons also, intellectuals have shown a tendency to exalt the market
for ideas and to depreciate the market for goods. Such an attitude seems
to me unjustified.}
\end{quote}

I argue, that not only is such a view unjustified but it is irredeemably
incoherent and irrational. In pointing out the tendency of intellectuals
to favor the market for ideas over the market for goods, Coase was
echoing \citet{Hayek1945}, who wrote of ``the relative importance of the
different kinds of knowledge'' and the fact that ``one kind of
knowledge, namely, scientific knowledge, occupies now so prominent a
place in public imagination that we tend to forget that it is not the
only kind that is relevant.'' Indeed, by taking advantage of relative
mispricings among commodities the financial trader benefits his fellow
men by allocating resources more efficiently. But this is hardly viewed
as a noble act, not nearly so noble as scientific discovery or academic
expression. Hayek saw keenly the situation:

\begin{quote}
\emph{It is a curious fact that this sort of knowledge should today be
generally regarded with a kind of contempt, and that someone who by such
knowledge gains an advantage over somebody better equipped with
theoretical or technical knowledge is thought to have acted almost
disreputably. To gain advantage from better knowledge of facilities of
communication or transport is sometimes regarded as almost dishonest,
although it is quite as important that society make use of the best
opportunities in this respect as in using the latest scientific
discoveries.}
\end{quote}

The lesson regarding the relative importance of different kinds of
knowledge that Hayek teaches is a very deep one. Indeed, when this
insight is fully appreciated one begins to see that the use of mundane
kinds of knowledge - Hayek's ``knowledge of time and place'' is
essential. It is not exaggeration to state that if the only knowledge
that society could usefully exploit was that from universities, the
press, literature and science we would all starve to death in very short
order. The financial arbitrageur is a perfect example of Hayek's ``man
on the spot'' and his actions benefit his fellows greatly. Still, when
one thinks of the abstract concept of the pursuit of knowledge, images
of the scientist in the lab or of the poet in the library come more
easily to mind than the trader scanning prices on his bank of monitors.
But for Hayek:

\begin{quote}
\emph{the arbitrageur who gains from local differences of commodity
prices, {[}is{]} performing {[}an{]} eminently useful function based on
special knowledge of circumstances of the fleeting moment not known to
others.}
\end{quote}

The actions of the arbitrageur are indeed eminently useful! Consider the
commodities that we require in our daily lives such as sugar, coffee,
wheat, milk, and oil that come to us more efficiently and at lower cost
than would otherwise be the case if not for the actions of commodity
traders. In addition, because of financial traders retirement is secured
more soundly through investment. And risks are insured against,
eliminated and transferred through financial markets that we would
otherwise have to bear.

Hayek compared the price system to ``a kind of machinery for registering
change'' and as a ``system of telecommunications.'' Similarly,
\citet{Scarf1990} has made an analogy between the market institution and
a massively distributed analog computer that computes values in the form
of prices. Following this line of reasoning, all market processes are
knowledge processes. Therefore there is not sharp distinction between
the ``market for ideas'' and the ``market for goods'', as Coase referred
to them. They are simply both markets and differ only in their relative
kinds of knowledge. \citet{Sowell1996} has made this point quite
succinctly:

\begin{quote}
\emph{While market economies are often thought of as money economies,
they are still more so knowledge economies\ldots{} Economic transactions
are purchases and sales of knowledge.}
\end{quote}

\begin{quote}
\emph{After all, the cavemen had the same natural resources at their
disposal as we have today\ldots{} We are all in the business of buying
and selling knowledge from one another, because we are each so
profoundly ignorant of what it takes to complete the whole process of
which we are part.}
\end{quote}

The link between the market for ideas and the market for goods is
further strengthened by considering the work of the decision theorist
Robert Nau. For example, \citet{NauMcCardle1991} state that the
principle of no-arbitrage, which is fundamental in finance theory, is
the common foundation of decision theory, game theory and competitive
market theory. \citet{Nau1999} refers to this as Arbitrage Choice
Theory, following the Bayesian Dutch book arguments of
\citet{deFinetti1937}. A Dutch book is a situation in which an
individual holds incoherent beliefs (beliefs inconsistent with the basic
axioms of probability), and if forced to bet on them exposes themself to
a guaranteed loss. When market transactions are seen as knowledge
transactions, it becomes clear that a Dutch book is equivalent to
arbitrage - the good old fashioned kind often derided from the world of
finance. This leads to the Dutch book theorem, which the Cambridge
Dictionary of Philosophy (1999) defines as:

\begin{quote}
The proposition that anyone who (a) counts a bet on a proposition p as
fair if the odds correspond to his degree of belief that p is true and
who (b) is willing to make any combination of bets he would regard
individually as fair will be vulnerable to a Dutch book provided his
degrees of belief do not conform tot he axioms of the probability
calculus. Thus, anyone of whom (a) and (b) are true and whos degree of
belief in a disjuntion of two incompatible propositions is not equal to
the sum of his degrees of belief in the two propositions taken
individually would be vulnerable to a Dutch book.
\end{quote}

When a trader makes a profit by simultaneously buying and selling
financial securities to exploit relative mispricings, this arbitrage is
simply the exploitation of a Dutch book expressed as incoherent market
prices. Likewise the intellectual pursuit of knowledge, what Coase
called the ``market for ideas'' can be seen as the pursuit of arbitrage,
or Dutch books, in the existing body of academic knowledge. Consider a
young scholar who discovers an error in the received theory of their
specific academic domain, and who makes a name for themself by
publishing an article correcting the error in a reputable academic
journal. This can now be easily understood to be the exploitation of a
Dutch book, or intellectual arbitrage.

My argument can now be stated simply as follows. One cannot
simultaneously believe: (a) that the pursuit of academic or scientific
knowledge is inherently moral, and (b) that the pursuit of capitalist
profits through financial arbitrage is inherently immoral.

There is thus a logical defeator for the belief that arbitrage is
immoral. Financial arbitrage rests on the same moral foundation as
scholarship - the pursuit of knowledge - albeit in a more plain and
mundate way.

\newpage
\singlespacing 
\bibliography{master.bib}

\end{document}

### 2016-11-30 APEE/svm-rmarkdown-article-example.Rmd
Adding the APEE abstract write up.

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ./svm-latex-ms.tex
title: "A Pandoc Markdown Article Starter and Template"
thanks: "Replication files are available on the author's Github account (http://github.com/svmiller). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: svmille@clemson.edu."
author:
- name: Steven V. Miller
  affiliation: Clemson University
abstract: "This document provides an introduction to R Markdown, argues for its benefits, and presents a sample manuscript template intended for an academic audience. I include basic syntax to R Markdown and a minimal working example of how the analysis itself can be conducted within R with the `knitr` package."
keywords: "pandoc, r markdown, knitr"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
# spacing: double
bibliography: ./master.bib
biblio-style: apsr
---

# Introduction

Academic workflow, certainly in political science, is at a crossroads. The *American Journal of Political Science* (*AJPS*) announced a (my words) ["show your work" initiative](http://ajps.org/2015/03/26/the-ajps-replication-policy-innovations-and-revisions/) in which authors who are tentatively accepted for publication at the journal must hand over the raw code and data that produced the results shown in the manuscript. The editorial team at *AJPS* then reproduces the code from the manuscript. Pending successful replication, the manuscript moves toward publication. The *AJPS* might be at the fore of this movement, and it could be the most aggressive among political science journals, but other journals in our field have signed the joint [Data Access & Research Transparency](http://www.dartstatement.org/) (DART) initiative. This, at a bare minimum, requires uploading code from quantitatively-oriented published articles to in-house directories hosted by the journal or to services like [Dataverse](http://dataverse.org/).

There are workflow implications to the Lacour controversy as well. Political science, for the foreseeable future, will struggle with the extent of [the data fraud perpetrated by Michael Lacour](http://stanford.edu/~dbroock/broockman_kalla_aronow_lg_irregularities.pdf) in an article co-authored with Donald P. Green in *Science*, the general scientific journal of record in the United States. A failure to reproduce LaCour's results with different samples uncovered a comprehensive effort by LaCour to "fake" data that provided results to what we felt or believed to be true [(i.e. "truthiness")](http://chronicle.com/article/LAffaire-LaCour/230905/). However, [fake data can have real consequences](http://kieranhealy.org/blog/archives/2015/05/20/fake-science-real-consequences/) for both the researcher and those who want to learn from it and use it for various purposes. Even research done honestly may suffer the same fate if researchers are not diligent in their workflow.

These recent events underscore the DART push and cast a shadow over our workflow. However, good workflow has always been an issue in our discipline. Cloud storage services like [Dropbox](http://www.dropbox.com) are still relatively new among political scientists. Without cloud storage, previous workflow left open the possibility that work between a home computer and an office computer was lost as a function of a corrupted thumb drive, an overheated power supply, or, among other things, the wave of viruses that [would particularly affect Microsoft users every summer](http://money.cnn.com/2003/11/05/technology/microsoftbounty/). Social sciences, [unlike engineering](http://kieranhealy.org/blog/archives/2014/01/23/plain-text/), have traditionally relied on software like Microsoft Word for manuscript preparation though any word processor reduces workflow to a series of clicks and strokes on a keyboard. This is [a terrible way to track changes](http://www.nytimes.com/2013/04/19/opinion/krugman-the-excel-depression.html) or maintain version control. The addition of collaborators only compounds all the aforementioned issues. The proverbial left hand may not know what the right hand is doing.

I think there is reason for optimism. We only struggle with it now because we have tools like [R Markdown](http://rmarkdown.rstudio.com/) and [Pandoc](http://pandoc.org/), more generally, that make significant strides in workflow. LaTeX resolved earlier issues of corrupted binary files by reducing documents to raw markup that was little more than raw text and revisions that could be easily kept as ["commented" text](http://tex.stackexchange.com/questions/11177/how-to-write-hidden-notes-in-a-latex-file). However, for all its benefits (including pretty PDFs), [LaTeX is *ugly* code](http://www-rohan.sdsu.edu/~aty/bibliog/latex/gripe.html) and does not provide means of seamlessly working with the actual data analysis itself. R Markdown both eliminates markup and allows the author and her collaborators to write and reproduce the manuscript in one fell swoop.

# Getting Started with YAML

The lion's share of a R Markdown document will be raw text, though the front matter may be the most important part of the document. R Markdown uses [YAML](http://www.yaml.org/) for its metadata and the fields differ from [what an author would use for a Beamer presentation](http://svmiller.com/blog/2015/02/moving-from-beamer-to-r-markdown/). I provide a sample YAML metadata largely taken from this exact document and explain it below.

```{r eval=FALSE}
---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Dropbox/miscelanea/svm-r-markdown-templates/svm.latex.ms.tex
title: "A Pandoc Markdown Article Starter and Template"
thanks: "Replication files are available on the author's Github account..."
author:
- name: Steven V. Miller
  affiliation: Clemson University
- name: Mary Margaret Albright
  affiliation: Pendelton State University
- name: Rembrandt Q. Einstein
  affiliation: Springfield University
abstract: "This document provides an introduction to R Markdown, argues for its..."
keywords: "pandoc, r markdown, knitr"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
# spacing: double
bibliography: ~/Dropbox/master.bib
biblio-style: apsr
---
```

`output:` will tell R Markdown we want a PDF document rendered with LaTeX. Since we are adding a fair bit of custom options to this call, we specify `pdf_document:` on the next line (with, importantly, a two-space indent). We specify additional output-level options underneath it, each are indented with four spaces. `citation_package: natbib` tells R Markdown to use `natbib` to handle bibliographic citations.[^natbib] Thereafter, the next line (`keep_tex: true`) tells R Markdown to render a raw `.tex` file along with the PDF document. This is useful for both debugging and the publication stage, when the editorial team will ask for the raw `.tex` so that they could render it and later provide page proofs. The next line `fig_caption: true` tells R Markdown to make sure that whatever images are included in the document are treated as figures in which our caption in brackets in a Markdown call is treated as the caption in the figure. The next line (`latex_engine: pdflatex`) tells R Markdown to use pdflatex and not some other option like `lualatex`. For my template, I'm pretty sure this is mandatory.[^pdflatex]

[^natbib]: R Markdown can use Pandoc's native bibliography management system or even `biblatex`, but I've found that it chokes with some of the more advanced stuff I've done with my .bib file over the years. For example, I've been diligent about special characters (e.g. umlauts and acute accents) in author names in my .bib file, but Pandoc's native citation system will choke on these characters in a .bib file. I effectively need `natbib` for my own projects.
[^pdflatex]: The main reason I still use `pdflatex` (and most readers probably do as well) is because of LaTeX fonts. [Unlike others](http://www-rohan.sdsu.edu/~aty/bibliog/latex/gripe.html), I find standard LaTeX fonts to be appealing.

The next line (`template: ...`) tells R Markdown to use my custom LaTeX template.[^path] While I will own any errors in the code, I confess to "Frankensteining" this template from [the default LaTeX template](https://github.com/jgm/pandoc-templates) from Pandoc, [Kieran Healy's LaTeX template](https://github.com/kjhealy/pandoc-templates/tree/master/templates), and liberally using raw TeX from the [Association for Computing Machinery's (ACM) LaTeX template](https://www.acm.org/publications/article-templates/acm-latex-style-guide). I rather like that template since it resembles standard manuscripts when they are published in some of our more prominent journals. I will continue with a description of the YAML metadata in the next paragraph, though invite the curious reader to scroll to the end of the accompanying post to see the PDF this template produces.

[^path]: Notice that the path is relative. The user can, if she wishes, install this in the default Pandoc directory. I don't think this is necessary. Just be mindful of wherever the template is placed. Importantly, `~` is used in R to find the home directory (not necessarily the working directory). It is equivalent to saying `/home/steve` in Linux, or `/Users/steve` on a Mac, in my case.

The next fields get to the heart of the document itself. `title:` is, intuitively, the title of the manuscript. Do note that fields like `title:` do not have to be in quotation marks, but must be in quotation marks if the title of the document includes a colon. That said, the only reason to use a colon in an article title is if it is followed by a subtitle, hence the optional field (`subtitle:`). Notice I "comment out" the subtitle in the above example with a pound sign since this particular document does not have a subtitle. If `thanks:` is included and has an accompanying entry, the ensuing title of the document gets an asterisk and a footnote. This field is typically used to advise readers that the document is a working paper or is forthcoming in a journal.

The next field (`author:`) is a divergence from standard YAML, but I think it is useful. I will also confess to pilfering this idea from Kieran Healy's template. Typically, multiple authors for a given document are separated by an `\and` in this field. However, standard LaTeX then creates a tabular field separating multiple authors that is somewhat restrictive and not easy to override. As a result, I use this setup (again, taken from Kieran Healy) to sidestep the restrictive rendering of authors in the standard `\maketitle` tag. After `author:`, enter `- name:` (no space before the dash) and fill in the field with the first author. On the next line, enter two spaces, followed by `affiliation:` and the institute or university affiliation of the first author.

Do notice this can be repeated for however many co-authors there are to a manuscript. The rendered PDF will enter each co-author in a new line in a manner similar to journals like *American Journal of Political Science*, *American Political Science Review*, or *Journal of Politics*.

The next two fields pertain to the frontmatter of a manuscript. They should also be intuitive for the reader. `abstract` should contain the abstract and `keywords` should contain some keywords that describe the research project. Both fields are optional, though are practically mandatory. Every manuscript requires an abstract and some journals---especially those published by Sage---request them with submitted manuscripts. My template also includes these keywords in the PDF's metadata.

`date` comes standard with R Markdown and you can use it to enter the date of the most recent compile. I typically include the date of the last compile for a working paper in the `thanks:` field, so this field currently does not do anything in my Markdown-LaTeX manuscript template. I include it in my YAML as a legacy, basically.

The next items are optional and cosmetic. `geometry:` is a standard option in LaTeX. I set the margins at one inch, and you probably should too. `fontfamily:` is optional, but I use it to specify the Palatino font. The default option is Computer Modern Roman. `fontsize:` sets, intuitively, the font size. The default is 10-point, but I prefer 11-point. `spacing:` is an optional field. If it is set as "double", the ensuing document is double-spaced. "single" is the only other valid entry for this field, though not including the entry in the YAML metadata amounts to singlespacing the document by default. Notice I have this "commented out" in the example code.

The final two options pertain to the bibliography. `bibliography:` specifies the location of the .bib file, so the author could make citations in the manuscript. `biblio-style` specifies the type of bibliography to use. You'll typically set this as APSR. You could also specify the relative path of [my *Journal of Peace Research* .bst file](http://svmiller.com/miscellany/journal-of-peace-research-bst-file/) if you are submitting to that journal.

# Getting Started with Markdown Syntax

There are a lot of cheatsheets and reference guides for Markdown (e.g. [Adam Prichard](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet), [Assemble](http://assemble.io/docs/Cheatsheet-Markdown.html), [Rstudio](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf), [Rstudio again](https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf), [Scott Boms](http://scottboms.com/downloads/documentation/markdown_cheatsheet.pdf), [Daring Fireball](https://daringfireball.net/projects/markdown/syntax), among, I'm sure, several others). I encourage the reader to look at those, though I will retread these references here with a minimal working example below.

```markdown

# Introduction

**Lorem ipsum** dolor *sit amet*.

- Single asterisks italicize text *like this*. 
- Double asterisks embolden text **like this**.

Start a new paragraph with a blank line separating paragraphs.

- This will start an unordered list environment, and this will be the first item.
- This will be a second item.
- A third item.
    - Four spaces and a dash create a sublist and this item in it.
- The fourth item.

1. This starts a numerical list.
2. This is no. 2 in the numerical list.

# This Starts A New Section
## This is a Subsection
### This is a Subsubsection
#### This starts a Paragraph Block.

> This will create a block quote, if you want one.

Want a table? This will create one.

Table Header  | Second Header
------------- | -------------
Table Cell    | Cell 2
Cell 3        | Cell 4

Note that the separators *do not* have to be aligned.

Want an image? This will do it.

![caption for my image](path/to/image.jpg)

`fig_caption: yes` will provide a caption. Put that in the YAML metadata.

Almost forgot about creating a footnote.[^1] This will do it again.[^2]

[^1]: The first footnote
[^2]: The second footnote

Want to cite something?

- Find your biblatexkey in your bib file.
- Put an @ before it, like @smith1984, or whatever it is.
- @smith1984 creates an in-text citation (e.g. Smith (1984) says...)
- [@smith1984] creates a parenthetical citation (Smith, 1984)

That'll also automatically create a reference list at the end of the document.

[In-text link to Google](http://google.com) as well.
```

That's honestly it. Markdown takes the chore of markup from your manuscript (hence: "Markdown").

On that note, you could easily pass most LaTeX code through Markdown if you're writing a LaTeX document. However, you don't need to do this (unless you're using the math environment) and probably shouldn't anyway if you intend to share your document in HTML as well.

# Using R Markdown with Knitr

Perhaps the greatest intrigue of R Markdown comes with the [`knitr` package](http://yihui.name/knitr/) provided by @xie2013ddrk. In other words, the author can, if she chooses, do the analysis in the Markdown document itself and compile/execute it in R.

Take, for example, this simple exercise using the `voteincome` data from the `Zelig` package. Suppose I want to explain the decision to vote using data from this package. I load in the data, clean the data, run the analyses, and present the results as a coefficient plot.

Here's what this code looks like. All I did was create a code display, which starts with three *backticks* (i.e. those ticks next to the number 1 key on your keyboard) and ends with three backticks on another line. On the first line of backticks (i.e. to start the code display) enter `{r, eval=FALSE, tidy=TRUE}`. The `eval=FALSE` option just displays the R code (and does not run it), `tidy=TRUE` wraps long code so it does not run off the page.

Within that code display, I enter my R code like this.

```{r, eval=FALSE, tidy = TRUE}
suppressMessages(library(Zelig))
suppressMessages(library(arm))
suppressMessages(library(coefplot))

data(voteincome)

voteincome$z.age <- arm::rescale(voteincome$age)
voteincome$z.education <- arm::rescale(voteincome$education)
voteincome$z.income <- arm::rescale(voteincome$income)

M1 <- glm(vote ~ z.age + female + z.education + z.income,
            data=voteincome, family=binomial)

coefplot(M1)
```

The implications for workflow are faily substantial. Authors can rather quickly display the code they used to run the analyses in the document itself (likely in the appendix). As such, there's little guesswork for reviewers and editors in understanding what the author did in the analyses reported in the manuscript.

It doesn't end there. In fact, here's what happens when `eval=FALSE` is omitted or changed to `eval=TRUE`. Now, the code runs within R. Observe.

```{r, eval=TRUE, tidy = TRUE, cache=FALSE, fig.cap="A Coefficient Plot"}
suppressMessages(library(Zelig))
suppressMessages(library(arm))

data(voteincome)

voteincome$z.age <- arm::rescale(voteincome$age)
voteincome$z.education <- arm::rescale(voteincome$education)
voteincome$z.income <- arm::rescale(voteincome$income)

M1 <- glm(vote ~ z.age + female + z.education + z.income,
            data=voteincome, family=binomial)

arm::coefplot(M1)
```

To get `knitr` to present the results of a table, add `results="asis"` to the brackets to start the R code chunk. The ensuing output will look like this (though the table may come on the next page).

```{r, eval=TRUE, tidy = TRUE, size="small", cache=FALSE, results="asis"}
suppressMessages(library(Zelig))
suppressMessages(library(stargazer))
suppressMessages(library(arm))

data(voteincome)

voteincome$z.age <- arm::rescale(voteincome$age)
voteincome$z.education <- arm::rescale(voteincome$education)
voteincome$z.income <- arm::rescale(voteincome$income)

M1 <- glm(vote ~ z.age + female + z.education + z.income,
            data=voteincome, family=binomial)

stargazer(M1, title="A Handsome Table", header=FALSE)
```

Adding `echo="FALSE"` inside the brackets to start the R chunk will omit the presentation of the R commands. It will just present the table. This provides substantial opportunity for authors in doing their analyses. Now, the analysis and presentation in the form of a polished manuscript can be effectively simultaneous.[^4]

[^4]: I'm not sure if I'm ready to commit to this myself since my workflow is still largely derived from [Rob J. Hyndman's example](http://robjhyndman.com/hyndsight/workflow-in-r/). However, *knitr* has endless potential, especially when analyses can stored in cache, saved as chunks, or loaded in the preamble of a document to reference later in the manuscript.

<!--
# References
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\vspace*{-0.2in}
\noindent
-->

### 2016-11-30 APEE/svm-rmarkdown-article-example.tex
Adding the APEE abstract write up.

\documentclass[11pt,]{article}
\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}

  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}

\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center

\renewenvironment{abstract}
 {{%
    \setlength{\leftmargin}{0mm}
    \setlength{\rightmargin}{\leftmargin}%
  }%
  \relax}
 {\endlist}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother

\setcounter{secnumdepth}{0}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\ImportTok}[1]{{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{{#1}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{{#1}}}}
\newcommand{\BuiltInTok}[1]{{#1}}
\newcommand{\ExtensionTok}[1]{{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}

\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

\title{A Pandoc Markdown Article Starter and Template \thanks{Replication files are available on the author's Github account
(\url{http://github.com/svmiller}). \textbf{Current version}: November
30, 2016; \textbf{Corresponding author}:
\href{mailto:svmille@clemson.edu}{\nolinkurl{svmille@clemson.edu}}.}  }

\author{\Large Steven V. Miller\vspace{0.05in} \newline\normalsize\emph{Clemson University}  }

\date{}

\usepackage{titlesec}

\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\itshape}
\titleformat*{\subsubsection}{\normalsize\itshape}
\titleformat*{\paragraph}{\normalsize\itshape}
\titleformat*{\subparagraph}{\normalsize\itshape}

\usepackage{natbib}
\bibliographystyle{apsr}

\newtheorem{hypothesis}{Hypothesis}
\usepackage{setspace}

\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Steven V. Miller (Clemson University)},
             pdfkeywords = {pandoc, r markdown, knitr},  
            pdftitle={A Pandoc Markdown Article Starter and Template},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}

% \pagenumbering{arabic}% resets `page` counter to 1 
%
% \maketitle

{% \usefont{T1}{pnc}{m}{n}
\setlength{\parindent}{0pt}
\thispagestyle{plain}
{\fontsize{18}{20}\selectfont\raggedright 
\maketitle  % title \par

}

{
   \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
\textbf{\authorfont Steven V. Miller} \hskip 15pt \emph{\small Clemson University}

}

}

\begin{abstract}

    \hbox{\vrule height .2pt width 39.14pc}

    \vskip 8.5pt % \small

\noindent This document provides an introduction to R Markdown, argues for its
benefits, and presents a sample manuscript template intended for an
academic audience. I include basic syntax to R Markdown and a minimal
working example of how the analysis itself can be conducted within R
with the \texttt{knitr} package.

\vskip 8.5pt \noindent \emph{Keywords}: pandoc, r markdown, knitr \par

    \hbox{\vrule height .2pt width 39.14pc}

\end{abstract}

\vskip 6.5pt

\noindent  \section{Introduction}\label{introduction}

Academic workflow, certainly in political science, is at a crossroads.
The \emph{American Journal of Political Science} (\emph{AJPS}) announced
a (my words)
\href{http://ajps.org/2015/03/26/the-ajps-replication-policy-innovations-and-revisions/}{``show
your work'' initiative} in which authors who are tentatively accepted
for publication at the journal must hand over the raw code and data that
produced the results shown in the manuscript. The editorial team at
\emph{AJPS} then reproduces the code from the manuscript. Pending
successful replication, the manuscript moves toward publication. The
\emph{AJPS} might be at the fore of this movement, and it could be the
most aggressive among political science journals, but other journals in
our field have signed the joint
\href{http://www.dartstatement.org/}{Data Access \& Research
Transparency} (DART) initiative. This, at a bare minimum, requires
uploading code from quantitatively-oriented published articles to
in-house directories hosted by the journal or to services like
\href{http://dataverse.org/}{Dataverse}.

There are workflow implications to the Lacour controversy as well.
Political science, for the foreseeable future, will struggle with the
extent of
\href{http://stanford.edu/~dbroock/broockman_kalla_aronow_lg_irregularities.pdf}{the
data fraud perpetrated by Michael Lacour} in an article co-authored with
Donald P. Green in \emph{Science}, the general scientific journal of
record in the United States. A failure to reproduce LaCour's results
with different samples uncovered a comprehensive effort by LaCour to
``fake'' data that provided results to what we felt or believed to be
true \href{http://chronicle.com/article/LAffaire-LaCour/230905/}{(i.e.
``truthiness'')}. However,
\href{http://kieranhealy.org/blog/archives/2015/05/20/fake-science-real-consequences/}{fake
data can have real consequences} for both the researcher and those who
want to learn from it and use it for various purposes. Even research
done honestly may suffer the same fate if researchers are not diligent
in their workflow.

These recent events underscore the DART push and cast a shadow over our
workflow. However, good workflow has always been an issue in our
discipline. Cloud storage services like
\href{http://www.dropbox.com}{Dropbox} are still relatively new among
political scientists. Without cloud storage, previous workflow left open
the possibility that work between a home computer and an office computer
was lost as a function of a corrupted thumb drive, an overheated power
supply, or, among other things, the wave of viruses that
\href{http://money.cnn.com/2003/11/05/technology/microsoftbounty/}{would
particularly affect Microsoft users every summer}. Social sciences,
\href{http://kieranhealy.org/blog/archives/2014/01/23/plain-text/}{unlike
engineering}, have traditionally relied on software like Microsoft Word
for manuscript preparation though any word processor reduces workflow to
a series of clicks and strokes on a keyboard. This is
\href{http://www.nytimes.com/2013/04/19/opinion/krugman-the-excel-depression.html}{a
terrible way to track changes} or maintain version control. The addition
of collaborators only compounds all the aforementioned issues. The
proverbial left hand may not know what the right hand is doing.

I think there is reason for optimism. We only struggle with it now
because we have tools like \href{http://rmarkdown.rstudio.com/}{R
Markdown} and \href{http://pandoc.org/}{Pandoc}, more generally, that
make significant strides in workflow. LaTeX resolved earlier issues of
corrupted binary files by reducing documents to raw markup that was
little more than raw text and revisions that could be easily kept as
\href{http://tex.stackexchange.com/questions/11177/how-to-write-hidden-notes-in-a-latex-file}{``commented''
text}. However, for all its benefits (including pretty PDFs),
\href{http://www-rohan.sdsu.edu/~aty/bibliog/latex/gripe.html}{LaTeX is
\emph{ugly} code} and does not provide means of seamlessly working with
the actual data analysis itself. R Markdown both eliminates markup and
allows the author and her collaborators to write and reproduce the
manuscript in one fell swoop.

\section{Getting Started with YAML}\label{getting-started-with-yaml}

The lion's share of a R Markdown document will be raw text, though the
front matter may be the most important part of the document. R Markdown
uses \href{http://www.yaml.org/}{YAML} for its metadata and the fields
differ from
\href{http://svmiller.com/blog/2015/02/moving-from-beamer-to-r-markdown/}{what
an author would use for a Beamer presentation}. I provide a sample YAML
metadata largely taken from this exact document and explain it below.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{---}
\NormalTok{output:}\StringTok{ }
\StringTok{  }\NormalTok{pdf_document:}
\StringTok{    }\NormalTok{citation_package:}\StringTok{ }\NormalTok{natbib}
    \NormalTok{keep_tex:}\StringTok{ }\NormalTok{true}
    \NormalTok{fig_caption:}\StringTok{ }\NormalTok{true}
    \NormalTok{latex_engine:}\StringTok{ }\NormalTok{pdflatex}
    \NormalTok{template:}\StringTok{ }\ErrorTok{~/}\NormalTok{Dropbox/miscelanea/svm-r-markdown-templates/svm.latex.ms.tex}
\NormalTok{title:}\StringTok{ "A Pandoc Markdown Article Starter and Template"}
\NormalTok{thanks:}\StringTok{ "Replication files are available on the author's Github account..."}
\NormalTok{author:}
\NormalTok{-}\StringTok{ }\NormalTok{name:}\StringTok{ }\NormalTok{Steven V. Miller}
  \NormalTok{affiliation:}\StringTok{ }\NormalTok{Clemson University}
\NormalTok{-}\StringTok{ }\NormalTok{name:}\StringTok{ }\NormalTok{Mary Margaret Albright}
  \NormalTok{affiliation:}\StringTok{ }\NormalTok{Pendelton State University}
\NormalTok{-}\StringTok{ }\NormalTok{name:}\StringTok{ }\NormalTok{Rembrandt Q. Einstein}
  \NormalTok{affiliation:}\StringTok{ }\NormalTok{Springfield University}
\NormalTok{abstract:}\StringTok{ "This document provides an introduction to R Markdown, argues for its..."}
\NormalTok{keywords:}\StringTok{ "pandoc, r markdown, knitr"}
\NormalTok{date:}\StringTok{ "`r format(Sys.time(), '%B %d, %Y')`"}
\NormalTok{geometry:}\StringTok{ }\NormalTok{margin=1in}
\NormalTok{fontfamily:}\StringTok{ }\NormalTok{mathpazo}
\NormalTok{fontsize:}\StringTok{ }\NormalTok{11pt}
\CommentTok{# spacing: double}
\NormalTok{bibliography:}\StringTok{ }\ErrorTok{~/}\NormalTok{Dropbox/master.bib}
\NormalTok{biblio-style:}\StringTok{ }\NormalTok{apsr}
\NormalTok{---}
\end{Highlighting}
\end{Shaded}

\texttt{output:} will tell R Markdown we want a PDF document rendered
with LaTeX. Since we are adding a fair bit of custom options to this
call, we specify \texttt{pdf\_document:} on the next line (with,
importantly, a two-space indent). We specify additional output-level
options underneath it, each are indented with four spaces.
\texttt{citation\_package:\ natbib} tells R Markdown to use
\texttt{natbib} to handle bibliographic citations.\footnote{R Markdown
  can use Pandoc's native bibliography management system or even
  \texttt{biblatex}, but I've found that it chokes with some of the more
  advanced stuff I've done with my .bib file over the years. For
  example, I've been diligent about special characters (e.g.~umlauts and
  acute accents) in author names in my .bib file, but Pandoc's native
  citation system will choke on these characters in a .bib file. I
  effectively need \texttt{natbib} for my own projects.} Thereafter, the
next line (\texttt{keep\_tex:\ true}) tells R Markdown to render a raw
\texttt{.tex} file along with the PDF document. This is useful for both
debugging and the publication stage, when the editorial team will ask
for the raw \texttt{.tex} so that they could render it and later provide
page proofs. The next line \texttt{fig\_caption:\ true} tells R Markdown
to make sure that whatever images are included in the document are
treated as figures in which our caption in brackets in a Markdown call
is treated as the caption in the figure. The next line
(\texttt{latex\_engine:\ pdflatex}) tells R Markdown to use pdflatex and
not some other option like \texttt{lualatex}. For my template, I'm
pretty sure this is mandatory.\footnote{The main reason I still use
  \texttt{pdflatex} (and most readers probably do as well) is because of
  LaTeX fonts.
  \href{http://www-rohan.sdsu.edu/~aty/bibliog/latex/gripe.html}{Unlike
  others}, I find standard LaTeX fonts to be appealing.}

The next line (\texttt{template:\ ...}) tells R Markdown to use my
custom LaTeX template.\footnote{Notice that the path is relative. The
  user can, if she wishes, install this in the default Pandoc directory.
  I don't think this is necessary. Just be mindful of wherever the
  template is placed. Importantly, \texttt{\textasciitilde{}} is used in
  R to find the home directory (not necessarily the working directory).
  It is equivalent to saying \texttt{/home/steve} in Linux, or
  \texttt{/Users/steve} on a Mac, in my case.} While I will own any
errors in the code, I confess to ``Frankensteining'' this template from
\href{https://github.com/jgm/pandoc-templates}{the default LaTeX
template} from Pandoc,
\href{https://github.com/kjhealy/pandoc-templates/tree/master/templates}{Kieran
Healy's LaTeX template}, and liberally using raw TeX from the
\href{https://www.acm.org/publications/article-templates/acm-latex-style-guide}{Association
for Computing Machinery's (ACM) LaTeX template}. I rather like that
template since it resembles standard manuscripts when they are published
in some of our more prominent journals. I will continue with a
description of the YAML metadata in the next paragraph, though invite
the curious reader to scroll to the end of the accompanying post to see
the PDF this template produces.

The next fields get to the heart of the document itself. \texttt{title:}
is, intuitively, the title of the manuscript. Do note that fields like
\texttt{title:} do not have to be in quotation marks, but must be in
quotation marks if the title of the document includes a colon. That
said, the only reason to use a colon in an article title is if it is
followed by a subtitle, hence the optional field (\texttt{subtitle:}).
Notice I ``comment out'' the subtitle in the above example with a pound
sign since this particular document does not have a subtitle. If
\texttt{thanks:} is included and has an accompanying entry, the ensuing
title of the document gets an asterisk and a footnote. This field is
typically used to advise readers that the document is a working paper or
is forthcoming in a journal.

The next field (\texttt{author:}) is a divergence from standard YAML,
but I think it is useful. I will also confess to pilfering this idea
from Kieran Healy's template. Typically, multiple authors for a given
document are separated by an \texttt{\textbackslash{}and} in this field.
However, standard LaTeX then creates a tabular field separating multiple
authors that is somewhat restrictive and not easy to override. As a
result, I use this setup (again, taken from Kieran Healy) to sidestep
the restrictive rendering of authors in the standard
\texttt{\textbackslash{}maketitle} tag. After \texttt{author:}, enter
\texttt{-\ name:} (no space before the dash) and fill in the field with
the first author. On the next line, enter two spaces, followed by
\texttt{affiliation:} and the institute or university affiliation of the
first author.

Do notice this can be repeated for however many co-authors there are to
a manuscript. The rendered PDF will enter each co-author in a new line
in a manner similar to journals like \emph{American Journal of Political
Science}, \emph{American Political Science Review}, or \emph{Journal of
Politics}.

The next two fields pertain to the frontmatter of a manuscript. They
should also be intuitive for the reader. \texttt{abstract} should
contain the abstract and \texttt{keywords} should contain some keywords
that describe the research project. Both fields are optional, though are
practically mandatory. Every manuscript requires an abstract and some
journals---especially those published by Sage---request them with
submitted manuscripts. My template also includes these keywords in the
PDF's metadata.

\texttt{date} comes standard with R Markdown and you can use it to enter
the date of the most recent compile. I typically include the date of the
last compile for a working paper in the \texttt{thanks:} field, so this
field currently does not do anything in my Markdown-LaTeX manuscript
template. I include it in my YAML as a legacy, basically.

The next items are optional and cosmetic. \texttt{geometry:} is a
standard option in LaTeX. I set the margins at one inch, and you
probably should too. \texttt{fontfamily:} is optional, but I use it to
specify the Palatino font. The default option is Computer Modern Roman.
\texttt{fontsize:} sets, intuitively, the font size. The default is
10-point, but I prefer 11-point. \texttt{spacing:} is an optional field.
If it is set as ``double'', the ensuing document is double-spaced.
``single'' is the only other valid entry for this field, though not
including the entry in the YAML metadata amounts to singlespacing the
document by default. Notice I have this ``commented out'' in the example
code.

The final two options pertain to the bibliography.
\texttt{bibliography:} specifies the location of the .bib file, so the
author could make citations in the manuscript. \texttt{biblio-style}
specifies the type of bibliography to use. You'll typically set this as
APSR. You could also specify the relative path of
\href{http://svmiller.com/miscellany/journal-of-peace-research-bst-file/}{my
\emph{Journal of Peace Research} .bst file} if you are submitting to
that journal.

\section{Getting Started with Markdown
Syntax}\label{getting-started-with-markdown-syntax}

There are a lot of cheatsheets and reference guides for Markdown (e.g.
\href{https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet}{Adam
Prichard},
\href{http://assemble.io/docs/Cheatsheet-Markdown.html}{Assemble},
\href{https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf}{Rstudio},
\href{https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf}{Rstudio
again},
\href{http://scottboms.com/downloads/documentation/markdown_cheatsheet.pdf}{Scott
Boms}, \href{https://daringfireball.net/projects/markdown/syntax}{Daring
Fireball}, among, I'm sure, several others). I encourage the reader to
look at those, though I will retread these references here with a
minimal working example below.

\begin{Shaded}
\begin{Highlighting}[]

\FunctionTok{# Introduction}

\NormalTok{**Lorem ipsum** dolor *sit amet*. }

\NormalTok{- }\FloatTok{Single asterisks italicize text *like this*. }
\FloatTok{- Double asterisks embolden text **like this**.}

\FloatTok{Start a new paragraph with a blank line separating paragraphs.}

\FloatTok{- This will start an unordered list environment, and this will be the first item.}
\FloatTok{- This will be a second item.}
\FloatTok{- A third item.}
\FloatTok{    - Four spaces and a dash create a sublist and this item in it.}
\FloatTok{- The fourth item.}
\FloatTok{  }  
\FloatTok{1. This starts a numerical list.}
\FloatTok{2. This is no. 2 in the numerical list.}
\FloatTok{  }  
\FloatTok{# This Starts A New Section}
\FloatTok{## This is a Subsection}
\FloatTok{### This is a Subsubsection}
\FloatTok{#### This starts a Paragraph Block.}

\FloatTok{> This will create a block quote, if you want one.}

\FloatTok{Want a table? This will create one.}

\FloatTok{Table Header  | Second Header}
\FloatTok{------------- | -------------}
\FloatTok{Table Cell    | Cell 2}
\FloatTok{Cell 3        | Cell 4 }

\FloatTok{Note that the separators *do not* have to be aligned.}

\FloatTok{Want an image? This will do it.}

\AlertTok{![caption for my image](path/to/image.jpg)}

\BaseNTok{`fig_caption: yes`}\FloatTok{ will provide a caption. Put that in the YAML metadata.}

\FloatTok{Almost forgot about creating a footnote.}\OtherTok{[^1]}\FloatTok{ This will do it again.}\OtherTok{[^2]}

\OtherTok{[^1]}\FloatTok{: The first footnote}
\OtherTok{[^2]}\FloatTok{: The second footnote}

\FloatTok{Want to cite something? }

\FloatTok{- Find your biblatexkey in your bib file.}
\FloatTok{- Put an @ before it, like @smith1984, or whatever it is.}
\FloatTok{- @smith1984 creates an in-text citation (e.g. Smith (1984) says...)}
\FloatTok{- [@smith1984] creates a parenthetical citation (Smith, 1984)}

\FloatTok{That'll also automatically create a reference list at the end of the document.}

\OtherTok{[In-text link to Google](http://google.com)}\FloatTok{ as well.}
\end{Highlighting}
\end{Shaded}

That's honestly it. Markdown takes the chore of markup from your
manuscript (hence: ``Markdown'').

On that note, you could easily pass most LaTeX code through Markdown if
you're writing a LaTeX document. However, you don't need to do this
(unless you're using the math environment) and probably shouldn't anyway
if you intend to share your document in HTML as well.

\section{Using R Markdown with Knitr}\label{using-r-markdown-with-knitr}

Perhaps the greatest intrigue of R Markdown comes with the
\href{http://yihui.name/knitr/}{\texttt{knitr} package} provided by
\citet{xie2013ddrk}. In other words, the author can, if she chooses, do
the analysis in the Markdown document itself and compile/execute it in
R.

Take, for example, this simple exercise using the \texttt{voteincome}
data from the \texttt{Zelig} package. Suppose I want to explain the
decision to vote using data from this package. I load in the data, clean
the data, run the analyses, and present the results as a coefficient
plot.

Here's what this code looks like. All I did was create a code display,
which starts with three \emph{backticks} (i.e.~those ticks next to the
number 1 key on your keyboard) and ends with three backticks on another
line. On the first line of backticks (i.e.~to start the code display)
enter \texttt{\{r,\ eval=FALSE,\ tidy=TRUE\}}. The \texttt{eval=FALSE}
option just displays the R code (and does not run it),
\texttt{tidy=TRUE} wraps long code so it does not run off the page.

Within that code display, I enter my R code like this.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{suppressMessages}\NormalTok{(}\KeywordTok{library}\NormalTok{(Zelig))}
\KeywordTok{suppressMessages}\NormalTok{(}\KeywordTok{library}\NormalTok{(arm))}
\KeywordTok{suppressMessages}\NormalTok{(}\KeywordTok{library}\NormalTok{(coefplot))}

\KeywordTok{data}\NormalTok{(voteincome)}

\NormalTok{voteincome$z.age <-}\StringTok{ }\NormalTok{arm::}\KeywordTok{rescale}\NormalTok{(voteincome$age)}
\NormalTok{voteincome$z.education <-}\StringTok{ }\NormalTok{arm::}\KeywordTok{rescale}\NormalTok{(voteincome$education)}
\NormalTok{voteincome$z.income <-}\StringTok{ }\NormalTok{arm::}\KeywordTok{rescale}\NormalTok{(voteincome$income)}

\NormalTok{M1 <-}\StringTok{ }\KeywordTok{glm}\NormalTok{(vote ~}\StringTok{ }\NormalTok{z.age +}\StringTok{ }\NormalTok{female +}\StringTok{ }\NormalTok{z.education +}\StringTok{ }\NormalTok{z.income, }\DataTypeTok{data =} \NormalTok{voteincome, }
    \DataTypeTok{family =} \NormalTok{binomial)}

\KeywordTok{coefplot}\NormalTok{(M1)}
\end{Highlighting}
\end{Shaded}

The implications for workflow are faily substantial. Authors can rather
quickly display the code they used to run the analyses in the document
itself (likely in the appendix). As such, there's little guesswork for
reviewers and editors in understanding what the author did in the
analyses reported in the manuscript.

It doesn't end there. In fact, here's what happens when
\texttt{eval=FALSE} is omitted or changed to \texttt{eval=TRUE}. Now,
the code runs within R. Observe.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{suppressMessages}\NormalTok{(}\KeywordTok{library}\NormalTok{(Zelig))}
\KeywordTok{suppressMessages}\NormalTok{(}\KeywordTok{library}\NormalTok{(arm))}

\KeywordTok{data}\NormalTok{(voteincome)}

\NormalTok{voteincome$z.age <-}\StringTok{ }\NormalTok{arm::}\KeywordTok{rescale}\NormalTok{(voteincome$age)}
\NormalTok{voteincome$z.education <-}\StringTok{ }\NormalTok{arm::}\KeywordTok{rescale}\NormalTok{(voteincome$education)}
\NormalTok{voteincome$z.income <-}\StringTok{ }\NormalTok{arm::}\KeywordTok{rescale}\NormalTok{(voteincome$income)}

\NormalTok{M1 <-}\StringTok{ }\KeywordTok{glm}\NormalTok{(vote ~}\StringTok{ }\NormalTok{z.age +}\StringTok{ }\NormalTok{female +}\StringTok{ }\NormalTok{z.education +}\StringTok{ }\NormalTok{z.income, }\DataTypeTok{data =} \NormalTok{voteincome, }
    \DataTypeTok{family =} \NormalTok{binomial)}

\NormalTok{arm::}\KeywordTok{coefplot}\NormalTok{(M1)}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\centering
\includegraphics{svm-rmarkdown-article-example_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{A Coefficient Plot}
\end{figure}

To get \texttt{knitr} to present the results of a table, add
\texttt{results="asis"} to the brackets to start the R code chunk. The
ensuing output will look like this (though the table may come on the
next page).

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{suppressMessages}\NormalTok{(}\KeywordTok{library}\NormalTok{(Zelig))}
\KeywordTok{suppressMessages}\NormalTok{(}\KeywordTok{library}\NormalTok{(stargazer))}
\KeywordTok{suppressMessages}\NormalTok{(}\KeywordTok{library}\NormalTok{(arm))}

\KeywordTok{data}\NormalTok{(voteincome)}

\NormalTok{voteincome$z.age <-}\StringTok{ }\NormalTok{arm::}\KeywordTok{rescale}\NormalTok{(voteincome$age)}
\NormalTok{voteincome$z.education <-}\StringTok{ }\NormalTok{arm::}\KeywordTok{rescale}\NormalTok{(voteincome$education)}
\NormalTok{voteincome$z.income <-}\StringTok{ }\NormalTok{arm::}\KeywordTok{rescale}\NormalTok{(voteincome$income)}

\NormalTok{M1 <-}\StringTok{ }\KeywordTok{glm}\NormalTok{(vote ~}\StringTok{ }\NormalTok{z.age +}\StringTok{ }\NormalTok{female +}\StringTok{ }\NormalTok{z.education +}\StringTok{ }\NormalTok{z.income, }\DataTypeTok{data =} \NormalTok{voteincome, }
    \DataTypeTok{family =} \NormalTok{binomial)}

\KeywordTok{stargazer}\NormalTok{(M1, }\DataTypeTok{title =} \StringTok{"A Handsome Table"}\NormalTok{, }\DataTypeTok{header =} \OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[!htbp] \centering 
  \caption{A Handsome Table} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & vote \\ 
\hline \\[-1.8ex] 
 z.age & 0.575$^{***}$ \\ 
  & (0.151) \\ 
  & \\ 
 female & 0.310$^{**}$ \\ 
  & (0.151) \\ 
  & \\ 
 z.education & 0.459$^{**}$ \\ 
  & (0.184) \\ 
  & \\ 
 z.income & 0.739$^{***}$ \\ 
  & (0.170) \\ 
  & \\ 
 Constant & 1.706$^{***}$ \\ 
  & (0.110) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 1,500 \\ 
Log Likelihood & $-$592.801 \\ 
Akaike Inf. Crit. & 1,195.602 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

Adding \texttt{echo="FALSE"} inside the brackets to start the R chunk
will omit the presentation of the R commands. It will just present the
table. This provides substantial opportunity for authors in doing their
analyses. Now, the analysis and presentation in the form of a polished
manuscript can be effectively simultaneous.\footnote{I'm not sure if I'm
  ready to commit to this myself since my workflow is still largely
  derived from
  \href{http://robjhyndman.com/hyndsight/workflow-in-r/}{Rob J.
  Hyndman's example}. However, \emph{knitr} has endless potential,
  especially when analyses can stored in cache, saved as chunks, or
  loaded in the preamble of a document to reference later in the
  manuscript.}

\newpage
\singlespacing 
\bibliography{master.bib}

\end{document}

### 2017-04-22 Draft/draft.Rmd
Adding thoughts and renderer script.

--- 2016-11-30 APEE/morality-of-arbitrage-abstract.Rmd
@@
 
+> [T]he shipper who earns his living from using otherwise empty or half-filled journeys of tramp-steamers, or the estate
+> agent whose whole knowledge is almost exclusively one of temporary opportunities, or the *arbitrageur* who gains from
+> local differences of commodity prices, are all performing eminently useful functions based on special knowledge of
+> circumstances of the fleeting moment not known to others.
+	-- F.A. Hayek
+
 The pursuit of knowledge through academic scholarship rests on a commonly held moral foundation.
@@
 Such a firm makes its profits, often astonishingly large profits, by buying and selling financial securities and profiting from speculation.
-A common line is of reasoning is that such a firm is predatory, parasitic, and even rapacious and as such cannot possibly be acting morally.
+A common line of reasoning is that such a firm is predatory, parasitic, and even rapacious and as such cannot possibly be acting morally.
 
@@
 
+# Dutch Books
+
+#
+
 <!--

### 2017-04-22 Draft/draft.tex
Adding thoughts and renderer script.

--- 2016-11-30 APEE/morality-of-arbitrage-abstract.tex
@@
 
+\begin{quote}
+{[}T{]}he shipper who earns his living from using otherwise empty or
+half-filled journeys of tramp-steamers, or the estate agent whose whole
+knowledge is almost exclusively one of temporary opportunities, or the
+\emph{arbitrageur} who gains from local differences of commodity prices,
+are all performing eminently useful functions based on special knowledge
+of circumstances of the fleeting moment not known to others. -- F.A.
+Hayek
+\end{quote}
+
 The pursuit of knowledge through academic scholarship rests on a
@@
 profits, often astonishingly large profits, by buying and selling
-financial securities and profiting from speculation. A common line is of
+financial securities and profiting from speculation. A common line of
 reasoning is that such a firm is predatory, parasitic, and even
@@
 
+\section{Dutch Books}\label{dutch-books}
+
+\section{}\label{section}
+
 \newpage

### 2017-04-22 Draft/draft2.Rmd
Adding draft2.

--- 2017-04-22 Draft/draft.Rmd
@@
 
-The pursuit of knowledge through academic scholarship rests on a commonly held moral foundation.
-The pursuit of truth, which is widely believed to be the goal of scholarship, is thought to be an inherently moral activity.
-At the same time, it is an increasingly widely held belief that financial market arbitrage, the kind pursued by Wall Street traders, is an inherently immoral activity.
-Take for example, the case of the quantitative proprietary trading firm which serves no clients and which invests only the capital of its principals.
-Such a firm makes its profits, often astonishingly large profits, by buying and selling financial securities and profiting from speculation.
-A common line of reasoning is that such a firm is predatory, parasitic, and even rapacious and as such cannot possibly be acting morally.
+In this essay I follow the lead of @Coase1974, and examine the very common differential treatment of the market for goods and the market for ideas.
 
-In this paper, I argue that one cannot simultaneously hold the above two positions without behaving incoherently.
-The process of scholarship and financial trading are both examples of finding and exploiting Dutch books.
-Dutch books are simply arbitrage by another name.
-Thus scholarship can be seen, indeed is most properly seen, as a form of intellectual arbitrage.
-Just as traders find mispricings in financial securities and exploit them for financial profit, scholars find misunderstandings - mispricings by another name - and exploit them to establish their scholarly reputation.
+The plan of this paper is as follows: section 2 introduces Coases's original argument, and his conclusion that
+their different treatment is incongruous; section 3 discusses the view in @Hayek1945 that the essential
+nature of the economic problem is one of the utilization of knowledge. For Hayek, the economic process is an
+information process and markets can be seen, using the modern parlance, as information systems. There is thus
+no justification for the differential treatment of goods and ideas; section 4 introduces the concept of
+subjective probability following @deFinetti1937, as well as the Arbitrage Choice Theory outlined in @Nau1999;
+section 5 explains, as essential background, the Dutch Book Theorem; section 6 gives a few chosen examples of
+scholarly debates framed as Dutch Book arguments; section 6 frames Coases's original argument as a Dutch Book
+argument; section 7 concludes.
 
-@Coase1974, in what he referred to as the economics of the First Amendment, makes a similar argument by comparing the "market for ideas" and the more mundane "market for goods." In his analysis he points out a broad inconsistency in the way these two different markets are viewed: that the market for goods is inefficient and requires government regulation to tame it, but that it would even be immoral for government to seek to regulate the market for ideas.
-Coase points out that this view is fundamentally inconsistent:
+# The Market for Goods and the Market for Ideas
 
-> _Consider the question of consumer ignorance which is commonly thought to be a justification for government intervention.
-It is hard to believe that the general public is in a better position to evaluate competing views on economic and social policy than to choose between different kinds of food._
+# The Use of Knowledge in Society
 
-Coase states further:
+# Arbitrage Choice Theory
 
-> _Because of the view that a free market in ideas is necessary to the maintenance of democratic institutions and, I believe, for other reasons also, intellectuals have shown a tendency to exalt the market for ideas and to depreciate the market for goods.
-Such an attitude seems to me unjustified._
+# The Dutch Book Theorem Explained
 
-I argue, that not only is such a view unjustified but it is irredeemably incoherent and irrational.
-In pointing out the tendency of intellectuals to favor the market for ideas over the market for goods, Coase was echoing @Hayek1945, who wrote of "the relative importance of the different kinds of knowledge" and the fact that "one kind of knowledge, namely, scientific knowledge, occupies now so prominent a place in public imagination that we tend to forget that it is not the only kind that is relevant." Indeed, by taking advantage of relative mispricings among commodities the financial trader benefits his fellow men by allocating resources more efficiently.
-But this is hardly viewed as a noble act, not nearly so noble as scientific discovery or academic expression.
-Hayek saw keenly the situation:
+## Examples of Dutch Book Arguments
 
-> _It is a curious fact that this sort of knowledge should today be generally regarded with a kind of contempt, and that someone who by such knowledge gains an advantage over somebody better equipped with theoretical or technical knowledge is thought to have acted almost disreputably.
-To gain advantage from better knowledge of facilities of communication or transport is sometimes regarded as almost dishonest, although it is quite as important that society make use of the best opportunities in this respect as in using the latest scientific discoveries._
+# Coase's Dutch Book Argument
 
-The lesson regarding the relative importance of different kinds of knowledge that Hayek teaches is a very deep one.
-Indeed, when this insight is fully appreciated one begins to see that the use of mundane kinds of knowledge - Hayek's "knowledge of time and place" is essential.
-It is not exaggeration to state that if the only knowledge that society could usefully exploit was that from universities, the press, literature and science we would all starve to death in very short order.
-The financial arbitrageur is a perfect example of Hayek's "man on the spot" and his actions benefit his fellows greatly.
-Still, when one thinks of the abstract concept of the pursuit of knowledge, images of the scientist in the lab or of the poet in the library come more easily to mind than the trader scanning prices on his bank of monitors.
-But for Hayek:
-
-> _the arbitrageur who gains from local differences of commodity prices, [is] performing [an] eminently useful function based on special knowledge of circumstances of the fleeting moment not known to others._
-
-The actions of the arbitrageur are indeed eminently useful!
-Consider the commodities that we require in our daily lives such as sugar, coffee, wheat, milk, and oil that come to us more efficiently and at lower cost than would otherwise be the case if not for the actions of commodity traders.
-In addition, because of financial traders retirement is secured more soundly through investment.
-And risks are insured against, eliminated and transferred through financial markets that we would otherwise have to bear.
-
-Hayek compared the price system to "a kind of machinery for registering change" and as a "system of telecommunications." Similarly, @Scarf1990 has made an analogy between the market institution and a massively distributed analog computer that computes values in the form of prices.
-Following this line of reasoning, all market processes are knowledge processes.
-Therefore there is not sharp distinction between the "market for ideas" and the "market for goods", as Coase referred to them.
-They are simply both markets and differ only in their relative kinds of knowledge.
-@Sowell1996 has made this point quite succinctly:
-
-> _While market economies are often thought of as money economies, they are still more so knowledge economies... Economic transactions are purchases and sales of knowledge._
-
-> _After all, the cavemen had the same natural resources at their disposal as we have today...
-We are all in the business of buying and selling knowledge from one another, because we are each so profoundly ignorant of what it takes to complete the whole process of which we are part._
-
-The link between the market for ideas and the market for goods is further strengthened by considering the work of the decision theorist Robert Nau.
-For example, @NauMcCardle1991 state that the principle of no-arbitrage, which is fundamental in finance theory, is the common foundation of decision theory, game theory and competitive market theory.
-@Nau1999 refers to this as Arbitrage Choice Theory, following the Bayesian Dutch book arguments of @deFinetti1937.
-A Dutch book is a situation in which an individual holds incoherent beliefs (beliefs inconsistent with the basic axioms of probability), and if forced to bet on them exposes themself to a guaranteed loss.
-When market transactions are seen as knowledge transactions, it becomes clear that a Dutch book is equivalent to arbitrage - the good old fashioned kind often derided from the world of finance.
-This leads to the Dutch book theorem, which the Cambridge Dictionary of Philosophy (1999) defines as:
-
-> The proposition that anyone who (a) counts a bet on a proposition p as fair if the odds correspond to his degree of belief that p is true and who (b) is willing to make any combination of bets he would regard individually as fair will be vulnerable to a Dutch book provided his degrees of belief do not conform tot he axioms of the probability calculus.
-Thus, anyone of whom (a) and (b) are true and whos degree of belief in a disjuntion of two incompatible propositions is not equal to the sum of his degrees of belief in the two propositions taken individually would be vulnerable to a Dutch book.
-
-When a trader makes a profit by simultaneously buying and selling financial securities to exploit relative mispricings, this arbitrage is simply the exploitation of a Dutch book expressed as incoherent market prices.
-Likewise the intellectual pursuit of knowledge, what Coase called the "market for ideas" can be seen as the pursuit of arbitrage, or Dutch books, in the existing body of academic knowledge.
-Consider a young scholar who discovers an error in the received theory of their specific academic domain, and who makes a name for themself by publishing an article correcting the error in a reputable academic journal.
-This can now be easily understood to be the exploitation of a Dutch book, or intellectual arbitrage.
-
-My argument can now be stated simply as follows.
-One cannot simultaneously believe: (a) that the pursuit of academic or scientific knowledge is inherently moral, and (b) that the pursuit of capitalist profits through financial arbitrage is inherently immoral.
-
-There is thus a logical defeator for the belief that arbitrage is immoral.
-Financial arbitrage rests on the same moral foundation as scholarship - the pursuit of knowledge - albeit in a more plain and mundate way.
-
-# Dutch Books
-
-#
+# Conclusion
 

### 2017-04-22 Draft/draft2.tex
Adding draft2.

--- 2017-04-22 Draft/draft.tex
@@
 
-The pursuit of knowledge through academic scholarship rests on a
-commonly held moral foundation. The pursuit of truth, which is widely
-believed to be the goal of scholarship, is thought to be an inherently
-moral activity. At the same time, it is an increasingly widely held
-belief that financial market arbitrage, the kind pursued by Wall Street
-traders, is an inherently immoral activity. Take for example, the case
-of the quantitative proprietary trading firm which serves no clients and
-which invests only the capital of its principals. Such a firm makes its
-profits, often astonishingly large profits, by buying and selling
-financial securities and profiting from speculation. A common line of
-reasoning is that such a firm is predatory, parasitic, and even
-rapacious and as such cannot possibly be acting morally.
+In this essay I follow the lead of \citet{Coase1974}, and examine the
+very common differential treatment of the market for goods and the
+market for ideas.
 
-In this paper, I argue that one cannot simultaneously hold the above two
-positions without behaving incoherently. The process of scholarship and
-financial trading are both examples of finding and exploiting Dutch
-books. Dutch books are simply arbitrage by another name. Thus
-scholarship can be seen, indeed is most properly seen, as a form of
-intellectual arbitrage. Just as traders find mispricings in financial
-securities and exploit them for financial profit, scholars find
-misunderstandings - mispricings by another name - and exploit them to
-establish their scholarly reputation.
+The plan of this paper is as follows: section 2 introduces Coases's
+original argument, and his conclusion that their different treatment is
+incongruous; section 3 discusses the view in \citet{Hayek1945} that the
+essential nature of the economic problem is one of the utilization of
+knowledge. For Hayek, the economic process is an information process and
+markets can be seen, using the modern parlance, as information systems.
+There is thus no justification for the differential treatment of goods
+and ideas; section 4 introduces the concept of subjective probability
+following \citet{deFinetti1937}, as well as the Arbitrage Choice Theory
+outlined in \citet{Nau1999}; section 5 explains, as essential
+background, the Dutch Book Theorem; section 6 gives a few chosen
+examples of scholarly debates framed as Dutch Book arguments; section 6
+frames Coases's original argument as a Dutch Book argument; section 7
+concludes.
 
-\citet{Coase1974}, in what he referred to as the economics of the First
-Amendment, makes a similar argument by comparing the ``market for
-ideas'' and the more mundane ``market for goods.'' In his analysis he
-points out a broad inconsistency in the way these two different markets
-are viewed: that the market for goods is inefficient and requires
-government regulation to tame it, but that it would even be immoral for
-government to seek to regulate the market for ideas. Coase points out
-that this view is fundamentally inconsistent:
+\section{The Market for Goods and the Market for
+Ideas}\label{the-market-for-goods-and-the-market-for-ideas}
 
-\begin{quote}
-\emph{Consider the question of consumer ignorance which is commonly
-thought to be a justification for government intervention. It is hard to
-believe that the general public is in a better position to evaluate
-competing views on economic and social policy than to choose between
-different kinds of food.}
-\end{quote}
+\section{The Use of Knowledge in
+Society}\label{the-use-of-knowledge-in-society}
 
-Coase states further:
+\section{Arbitrage Choice Theory}\label{arbitrage-choice-theory}
 
-\begin{quote}
-\emph{Because of the view that a free market in ideas is necessary to
-the maintenance of democratic institutions and, I believe, for other
-reasons also, intellectuals have shown a tendency to exalt the market
-for ideas and to depreciate the market for goods. Such an attitude seems
-to me unjustified.}
-\end{quote}
+\section{The Dutch Book Theorem
+Explained}\label{the-dutch-book-theorem-explained}
 
-I argue, that not only is such a view unjustified but it is irredeemably
-incoherent and irrational. In pointing out the tendency of intellectuals
-to favor the market for ideas over the market for goods, Coase was
-echoing \citet{Hayek1945}, who wrote of ``the relative importance of the
-different kinds of knowledge'' and the fact that ``one kind of
-knowledge, namely, scientific knowledge, occupies now so prominent a
-place in public imagination that we tend to forget that it is not the
-only kind that is relevant.'' Indeed, by taking advantage of relative
-mispricings among commodities the financial trader benefits his fellow
-men by allocating resources more efficiently. But this is hardly viewed
-as a noble act, not nearly so noble as scientific discovery or academic
-expression. Hayek saw keenly the situation:
+\subsection{Examples of Dutch Book
+Arguments}\label{examples-of-dutch-book-arguments}
 
-\begin{quote}
-\emph{It is a curious fact that this sort of knowledge should today be
-generally regarded with a kind of contempt, and that someone who by such
-knowledge gains an advantage over somebody better equipped with
-theoretical or technical knowledge is thought to have acted almost
-disreputably. To gain advantage from better knowledge of facilities of
-communication or transport is sometimes regarded as almost dishonest,
-although it is quite as important that society make use of the best
-opportunities in this respect as in using the latest scientific
-discoveries.}
-\end{quote}
+\section{Coase's Dutch Book Argument}\label{coases-dutch-book-argument}
 
-The lesson regarding the relative importance of different kinds of
-knowledge that Hayek teaches is a very deep one. Indeed, when this
-insight is fully appreciated one begins to see that the use of mundane
-kinds of knowledge - Hayek's ``knowledge of time and place'' is
-essential. It is not exaggeration to state that if the only knowledge
-that society could usefully exploit was that from universities, the
-press, literature and science we would all starve to death in very short
-order. The financial arbitrageur is a perfect example of Hayek's ``man
-on the spot'' and his actions benefit his fellows greatly. Still, when
-one thinks of the abstract concept of the pursuit of knowledge, images
-of the scientist in the lab or of the poet in the library come more
-easily to mind than the trader scanning prices on his bank of monitors.
-But for Hayek:
-
-\begin{quote}
-\emph{the arbitrageur who gains from local differences of commodity
-prices, {[}is{]} performing {[}an{]} eminently useful function based on
-special knowledge of circumstances of the fleeting moment not known to
-others.}
-\end{quote}
-
-The actions of the arbitrageur are indeed eminently useful! Consider the
-commodities that we require in our daily lives such as sugar, coffee,
-wheat, milk, and oil that come to us more efficiently and at lower cost
-than would otherwise be the case if not for the actions of commodity
-traders. In addition, because of financial traders retirement is secured
-more soundly through investment. And risks are insured against,
-eliminated and transferred through financial markets that we would
-otherwise have to bear.
-
-Hayek compared the price system to ``a kind of machinery for registering
-change'' and as a ``system of telecommunications.'' Similarly,
-\citet{Scarf1990} has made an analogy between the market institution and
-a massively distributed analog computer that computes values in the form
-of prices. Following this line of reasoning, all market processes are
-knowledge processes. Therefore there is not sharp distinction between
-the ``market for ideas'' and the ``market for goods'', as Coase referred
-to them. They are simply both markets and differ only in their relative
-kinds of knowledge. \citet{Sowell1996} has made this point quite
-succinctly:
-
-\begin{quote}
-\emph{While market economies are often thought of as money economies,
-they are still more so knowledge economies\ldots{} Economic transactions
-are purchases and sales of knowledge.}
-\end{quote}
-
-\begin{quote}
-\emph{After all, the cavemen had the same natural resources at their
-disposal as we have today\ldots{} We are all in the business of buying
-and selling knowledge from one another, because we are each so
-profoundly ignorant of what it takes to complete the whole process of
-which we are part.}
-\end{quote}
-
-The link between the market for ideas and the market for goods is
-further strengthened by considering the work of the decision theorist
-Robert Nau. For example, \citet{NauMcCardle1991} state that the
-principle of no-arbitrage, which is fundamental in finance theory, is
-the common foundation of decision theory, game theory and competitive
-market theory. \citet{Nau1999} refers to this as Arbitrage Choice
-Theory, following the Bayesian Dutch book arguments of
-\citet{deFinetti1937}. A Dutch book is a situation in which an
-individual holds incoherent beliefs (beliefs inconsistent with the basic
-axioms of probability), and if forced to bet on them exposes themself to
-a guaranteed loss. When market transactions are seen as knowledge
-transactions, it becomes clear that a Dutch book is equivalent to
-arbitrage - the good old fashioned kind often derided from the world of
-finance. This leads to the Dutch book theorem, which the Cambridge
-Dictionary of Philosophy (1999) defines as:
-
-\begin{quote}
-The proposition that anyone who (a) counts a bet on a proposition p as
-fair if the odds correspond to his degree of belief that p is true and
-who (b) is willing to make any combination of bets he would regard
-individually as fair will be vulnerable to a Dutch book provided his
-degrees of belief do not conform tot he axioms of the probability
-calculus. Thus, anyone of whom (a) and (b) are true and whos degree of
-belief in a disjuntion of two incompatible propositions is not equal to
-the sum of his degrees of belief in the two propositions taken
-individually would be vulnerable to a Dutch book.
-\end{quote}
-
-When a trader makes a profit by simultaneously buying and selling
-financial securities to exploit relative mispricings, this arbitrage is
-simply the exploitation of a Dutch book expressed as incoherent market
-prices. Likewise the intellectual pursuit of knowledge, what Coase
-called the ``market for ideas'' can be seen as the pursuit of arbitrage,
-or Dutch books, in the existing body of academic knowledge. Consider a
-young scholar who discovers an error in the received theory of their
-specific academic domain, and who makes a name for themself by
-publishing an article correcting the error in a reputable academic
-journal. This can now be easily understood to be the exploitation of a
-Dutch book, or intellectual arbitrage.
-
-My argument can now be stated simply as follows. One cannot
-simultaneously believe: (a) that the pursuit of academic or scientific
-knowledge is inherently moral, and (b) that the pursuit of capitalist
-profits through financial arbitrage is inherently immoral.
-
-There is thus a logical defeator for the belief that arbitrage is
-immoral. Financial arbitrage rests on the same moral foundation as
-scholarship - the pursuit of knowledge - albeit in a more plain and
-mundate way.
-
-\section{Dutch Books}\label{dutch-books}
-
-\section{}\label{section}
+\section{Conclusion}\label{conclusion}
 

### 2017-04-22 Draft/render.R

@@ -1,2 +1,2 @@
 library(rmarkdown)
-render("draft.Rmd")
+render("draft2.Rmd")

### 2017-04-23 Draft/draft2.tex
Updating draft2.

@@
 
-\noindent  \section{Introduction}\label{introduction}
-
-\begin{quote}
+\noindent  \begin{quote}
 {[}T{]}he shipper who earns his living from using otherwise empty or
@@
 \end{quote}
+
+\section{Introduction}\label{introduction}
 

### 2017-04-23 Draft/draft2.Rmd
Updating draft2.

@@
 fontsize: 11pt
-# spacing: double
+spacing: double
 bibliography: ./master.bib
@@
 ---
-
-# Introduction
 
@@
 	-- F.A. Hayek
+
+# Introduction
 

### 2017-04-23 Draft/draft2.tex
Updating draft2.

@@
 
-\noindent  \begin{quote}
+\noindent \doublespacing \begin{quote}
 {[}T{]}he shipper who earns his living from using otherwise empty or

### 2017-05-22 Draft/draft2.Rmd
Update draft2.Rmd

@@
 
+The dictionary definition of a Dutch book is the following:
+
+"A principle for dynamic decision-making situations that leads to a sequence of bets finishing in an inescapable loss, as in the case of a bookmaker always gaining from gambling on the outcome of horse races."[^1].
+
 # Coase's Dutch Book Argument
@@
 -->
+
+[^1]: See the Routledge Dictionary of Economics entry on "Dutch books."

### 2017-05-22 Draft/draft2.Rmd
Updating draft2.

--- 2017-04-23 Draft/draft2.Rmd
@@
 
+The dictionary definition of a Dutch book is the following:
+
+> "A principle for dynamic decision-making situations that leads to a sequence of bets finishing in an inescapable loss, as in the case of a bookmaker always gaining from gambling on the outcome of horse races."[^1].
+
 ## Examples of Dutch Book Arguments

### 2017-05-22 Draft/draft2.tex
Updating draft2.

@@
 
+The dictionary definition of a Dutch book is the following:
+
+\begin{quote}
+``A principle for dynamic decision-making situations that leads to a
+sequence of bets finishing in an inescapable loss, as in the case of a
+bookmaker always gaining from gambling on the outcome of horse
+races.''\footnote{See the Routledge Dictionary of Economics entry on
+  ``Dutch books.''}.
+\end{quote}
+
 \subsection{Examples of Dutch Book
@@
 \singlespacing 
-\bibliography{master.bib}
+\bibliography{master}
 

### 2017-05-23 Draft/draft2.Rmd
Update to draft2.Rmd

@@
 
+In the nomenclature of finance a Dutch book is an arbitrage and the person making a Dutch book against an opponent is called an arbitrageur.
+For de Finetti the bookmaker whose gain is certain in a given bet is no different than the trader who earns a guaranteed profit by buying low and selling high when an asset is mispriced.
+
+For de Finetti probabilities are prices. In modern finance theory prices are probabilities. In the end it is an equivalence.
+
+Once seen through the lens of subjective probability, it becomes clear that what applies to mispriced assets also applies to misplaced probabilities. They are both examples of incoherent beliefs.
+
 ## Examples of Dutch Book Arguments

### 2017-05-25 Draft/draft2.Rmd
Major update to draft2.Rmd

@@
 
-In this essay I follow the lead of @Coase1974, and examine the very common differential treatment of the market for goods and the market for ideas.
+The pursuit of knowledge through academic scholarship rests on a commonly held moral foundation.
+The pursuit of truth, which is widely believed to be the goal of scholarship, is thought to be an inherently moral activity.
+At the same time, it is an increasingly widely held belief that financial market arbitrage, the kind pursued by Wall Street traders, is an inherently immoral activity.
+Take for example, the case of the quantitative proprietary trading firm which serves no clients and which invests only the capital of its principals.
+Such a firm makes its profits, often astonishingly large profits, by buying and selling financial securities and profiting from speculation.
+A common line of reasoning is that such a firm is predatory, parasitic, and even rapacious and as such cannot possibly be acting morally.
 
-The plan of this paper is as follows: section 2 introduces Coases's original argument, and his conclusion that
-their different treatment is incongruous; section 3 discusses the view in @Hayek1945 that the essential
-nature of the economic problem is one of the utilization of knowledge. For Hayek, the economic process is an
-information process and markets can be seen, using the modern parlance, as information systems. There is thus
-no justification for the differential treatment of goods and ideas; section 4 introduces the concept of
-subjective probability following @deFinetti1937, as well as the Arbitrage Choice Theory outlined in @Nau1999;
-section 5 explains, as essential background, the Dutch Book Theorem; section 6 gives a few chosen examples of
-scholarly debates framed as Dutch Book arguments; section 6 frames Coases's original argument as a Dutch Book
-argument; section 7 concludes.
+In this paper, I argue that one cannot simultaneously hold the above two positions without behaving incoherently.
+The process of scholarship and financial trading are both examples of finding and exploiting Dutch books.
+Dutch books are simply arbitrage by another name.
+Thus scholarship can be seen, indeed is most properly seen, as a form of intellectual arbitrage.
+Just as traders find mispricings in financial securities and exploit them for financial profit, scholars find misunderstandings - mispricings by another name - and exploit them to establish their scholarly reputation.
+
+The paper is organized as follows.
+I outline an original discussion due to @Coase1974 of the "market for ideas" and the "market for goods," and discuss his conclusion that their different treatment is incongruous in Section 2.
+I then discuss the idea, due to @Hayek1945, that the economic process is an information process in its most essential treatment in Section 3.
+In Section 4 I outline the concept of subjective probability following @deFinetti1937, as well as Arbitrage Choice Theory put forward by @Nau1999.
+In Section 5 I explain the Dutch Book Theorem as essential background to my argument.
+I give a few chosen examples of scholarly debates framed as Dutch Book arguments in Section 6.
+In Section 7 I present my own Dutch book argument.
+Section 8 concludes the paper.
 
@@
 
-# The Use of Knowledge in Society
+@Coase1974 points out that there has been a common tradition of drawing a sharp distinction between the "market for goods" and the "market for ideas." The "market for ideas" is the domain of intellectuals and consists of speech, writing, and religious belief - activities covered by the First Amendment.
+Coase notes that the common view has been that the "market for goods" requires extensive regulation to promote public interest, while the "market for ideas" would be greatly harmed by such regulatory activity.
+He writes "the Western world, by and large, accepts the distinction and the policy recommendations that go with it." For Coase, such an attitude is unjustified.
+
+Coase writes that "...
+belief in a free market in ideas does not have the same roots as belief in the value of free trade in goods." And further that, "...
+this view of the peculiar status of the market for ideas has been nourished by a commitment to democracy as exemplified in the political institutions of the United States, for whose efficient working a market in ideas not subject to government regulation is considered essential." Speaking of intellectuals Coase highlights that "intellectuals have shown a tendency to exalt the market for ideas and to depreciate the market for goods." But why should this differential treatment be so?
+For Coase the distinction is invalid as "[t]here is no fundamental difference between these two markets." He goes on to argue that we should use the same approach for all markets when deciding upon public policy.
+
+For Coase the explanation for the tendency on the part of intellectuals to make a sharp distinction between the two markets is self-interest and self-esteem.
+In offering this explanation, he echoes the Public Choice literature: self-interest leads intellectuals to see themselves as the experts who will plan and implement the regulation of the market for goods, while self-esteem causes them to deny any role for regulation of their domain - the market for ideas.
+Coase urges intellectuals to "...
+adopt a more consistent view."[^1] Expressing his dismay at this situation he writes:
+
+> It is hard to believe that the general public is in a better position to evaluate competing views on economic and social policy than to choose between different kinds of food.
+
+Indeed, this is puzzling, as is the distinction between the ethical underpinnings of the two markets.
+The discussion in @Coase1974 is helpful in framing the current discussion.
+Most essential is the perspective that intellectuals operate within a market setting when producing and promoting their ideas.[^2] The sharp distinction between the two markets when it comes to the role of government regulation parallels the common sharp distinction of their respective moral nature.
+When the scholar operates in the "market for ideas" it is commonly believed that her efforts are inherently ethical, resting on a long history and strong tradition of common moral values.
+While it is often the case, especially among intellectuals, to depreciate the moral value of capitalist enterprise that is the domain of the financial trader.
+Echoing Coase I argue below that this practice is unfounded, and I urge the adoption of a more consistent view as there is no fundamental difference between the two activities.
+They are both examples of arbitrage within their respective domains.
+
+# The Informational Role of Prices
+
+Once the domain of intellectuals is seen as a market - the "market for ideas" - we can inquire about the special nature of markets to better understand their ethical foundation.
+The essential element is that competitive markets are mediated by prices, and prices serve as signals of information.
+As @Grossman1989 writes "[i]t is a common theme of most discussions of the competitive price system that prices convey information."[^3] This concept in its original formulation is due to @Hayek1945, who wrote
+
+> ***We must look at the price system as ...
+a mechanism for communicating information if we want to understand its real function***...
+The most significant fact about this system is the economy of knowledge with which it operates, or how little the individual participants need to know in order to be able to take the right action ...
+by a kind of symbol, only the most essential information is passed on..."
+
+For Hayek, the essential element of markets is that they are information systems, as we might say in the modern parlance.[^4] Hayek wrote in the midst of the so-called socialist calculation debate.
+The Polish economist Oskar Lange (see @Lange1936 and @Lange1937) argued that taking mathematical models of neoclassical economics seriously, the competitive allocation of the market could be replicated by a central planner making socialism a viable economic system.
+Hayek vehemently opposed this view highlighting that the would-be central planner faces an insurmountable knowledge problem because the knowledge that must be made use of for such planning is dispersed widely among many people, who each possess only an incomplete and partial knowledge.[^x]
+
+Similar to Coase, Hayek points out the tendency of some to make a sharp distinction between different kinds of knowledge.
+He writes "one kind of knowledge, namely, scientific knowledge, occupies now so prominent a place in public imagination that we tend to forget that it is not the only kind that is relevant." Indeed, by taking advantage of relative mispricings among commodities the financial trader benefits his fellow men by allocating resources more efficiently.
+But this is hardly viewed as a noble act, not nearly so noble as scientific discovery or academic expression.
+Hayek saw keenly the situation:
+
+> It is a curious fact that this sort of knowledge should today be generally regarded with a kind of contempt, and that someone who by such knowledge gains an advantage over somebody better equipped with theoretical or technical knowledge is thought to have acted almost disreputably.
+To gain advantage from better knowledge of facilities of communication or transport is sometimes regarded as almost dishonest, although it is quite as important that society make use of the best opportunities in this respect as in using the latest scientific discoveries.
+
+The lesson regarding the relative importance of different kinds of knowledge that Hayek teaches is a very deep one.
+Indeed, when this insight is fully appreciated one begins to see that the use of mundane kinds of knowledge - Hayek's "knowledge of time and place" is essential.
+It is not exaggeration to state that if the only knowledge that society could usefully exploit was that from universities, the press, literature and science we would all starve to death in very short order.
+The financial arbitrageur is a perfect example of Hayek's "man on the spot" and his actions benefit his fellows greatly.
+Still, when one thinks of the abstract concept of the pursuit of knowledge, images of the scientist in the lab or of the scholar in the library come more easily to mind than the trader scanning prices on his bank of monitors.
+But for Hayek:
+
+> the *arbitrageur* who gains from local differences of commodity prices, [is] performing [an] eminently useful function based on special knowledge of circumstances of the fleeting moment not known to others.
+
+The actions of the arbitrageur are indeed eminently useful!
+Consider the commodities that we require in our daily lives such as sugar, coffee, wheat, milk, and oil that come to us more efficiently and at lower cost than would otherwise be the case if not for the actions of commodity traders.
+In addition, because of financial traders retirement is secured more soundly through investment.
+And risks are insured against, eliminated and transferred through financial markets that we would otherwise have to bear.
+
+Hayek compared the price system to "a kind of machinery for registering change" and as a "system of telecommunications." Similarly, @Scarf1990 has made an analogy between the market institution and a massively distributed analog computer that computes values in the form of prices.
+Following this line of reasoning, all market processes are knowledge processes.
+Therefore there is no sharp distinction between the "market for ideas" and the "market for goods", as Coase referred to them.
+They are simply both markets and differ only in their relative kinds of knowledge.
+@Sowell1996 has made this point quite succinctly:
+
+> While market economies are often thought of as money economies, they are still more so knowledge economies... Economic transactions are purchases and sales of knowledge.
+
+> After all, the cavemen had the same natural resources at their disposal as we have today...
+We are all in the business of buying and selling knowledge from one another, because we are each so profoundly ignorant of what it takes to complete the whole process of which we are part.
+
+My argument, echoing Coase and augmented by a sound understanding of market processes as information processes from Hayek, is that we should adopt a more coherent view of the ethical and moral foundations of both markets, for they are fundamentally of the same nature.
 
@@
 
-# The Dutch Book Theorem Explained
+The link between the market for ideas and the market for goods is further strengthened by considering the work of the decision theorist Robert Nau.
+For example, @NauMcCardle1991 state that the principle of no-arbitrage, which is fundamental in finance theory, is the common foundation of decision theory, game theory and competitive market theory.
+@Nau1999 refers to this as *arbitrage choice theory* (ACT), following the Bayesian Dutch book arguments of @deFinetti1937.
+A Dutch book is a situation in which an individual holds incoherent beliefs (beliefs inconsistent with the basic axioms of probability), and if forced to bet on them exposes themselves to a guaranteed loss.
+When market transactions are seen as knowledge transactions, it becomes clear that a Dutch book is equivalent to arbitrage - the good old fashioned kind often derided from the world of finance.
+In ACT "...
+no-arbitage is the core principle of rationality which remains after economic models are stripped of their excess baggage of intrinsically unverifiable or empirically disconfirmed assumptions..." The arbitrageur is Hayek's "man on the spot" who provides a useful informational service by correcting incoherent price signals.
+This is true in commodities and financial assets as well as in
+
+When a trader makes a profit by simultaneously buying and selling financial securities to exploit relative mispricings, this arbitrage is simply the exploitation of a Dutch book expressed as incoherent market prices.
+Likewise the intellectual pursuit of knowledge, what Coase called the "market for ideas" can be seen as the pursuit of arbitrage, or Dutch books, in the existing body of academic knowledge.
+Consider a young scholar who discovers an error in the received theory of their specific academic domain, and who makes a name for themselves by publishing an article correcting the error in a reputable academic journal.
+This can now be easily understood to be the exploitation of a Dutch book, or intellectual arbitrage.
+
+## The Dutch Book Theorem Explained
+
+Coherence in de Finetti's definition of probability is the counterpart of the modern theory of no-arbitrage in finance.[^5] Interestingly, de Finetti took a very operational and economic approach to eliciting subjective probabilities.
+
+The axioms of probability which characterize any theory of probability arise logically from the
+condition that subjective probabilities function as prices obeying coherency (i.e. the arbitrage free
+conditions).
+
+Looking at problems of uncertainty as situations in which various contingent claims are traded is the key insight offered by the state-preference theory.
 
@@
 
-> "A principle for dynamic decision-making situations that leads to a sequence of bets finishing in an inescapable loss, as in the case of a bookmaker always gaining from gambling on the outcome of horse races."[^1].
+> "A principle for dynamic decision-making situations that leads to a sequence of bets finishing in an inescapable loss, as in the case of a bookmaker always gaining from gambling on the outcome of horse races."[^n].
+
+The following example serves to demonstrate the principle.
+Consider agent A's degree of belief regarding the flipping of a fair coin.
+The event space is represented by $S = \{H, T\}$ where $H$ represents 'heads' and $T$ represents 'tails.' Suppose A's degrees of belief are expressed as probabilities: $P(H) = 0.51 \quad \mbox{and} \quad P(T) = 0.51$.
+That is, A is willing to pay $\$0.51$ to receive $\$1$ in the event of a 'heads', and also $\$0.51$ to receive $\$1$ in the event of a 'tails.' It is easy to see that A is acting incoherently.
+The book maker will be willing to take both bets simultaneously.
+Either 'heads' or a 'tails' will occur, so if A offers both bets simultaneously she will be guaranteed to earn $\$1$.
+But the total of her bets is $\$1.02$, so net of her bets she will lose $\$0.02$ whatever the state of the world.
+A Dutch book has been made against her.
 
@@
 
-# Coase's Dutch Book Argument
+- Culp & Miller vs. Pirrong re: whether or not MG was a prudent hedger
+- Swinburne vs. Howson re: whether or not God exists
+
+- The morality of scholarship vs the morality of arbitrage is an example of a DBA.
+
+# The Dutch Book Argument
 
@@
 
-[^1]: See the Routledge Dictionary of Economics entry on "Dutch books."
+[^1]: For a book-length treatment of such tendencies on the part of intellectuals see @Sowell2009.
+[^2]: Elsewhere @Polanyi2000 has made a similar case.
+[^3]: See also @Kreps1988 who states that "the notion that prices contain and convey information is standard doctrine among economists."
+[^4]: Hayek wrote: "It is more than a metaphor to describe the price system as a kind of machinery for registering change, or a *system of telecommunications*." Emphasis added. 
+[^5]: See @PressaccoZiani2010.
+[^x]: @Polanyi2000 makes a similar argument regarding a knowledge problem in science.
+He writes: "Any attempt to organize the group ...
+under a single authority would eliminate their independent initiatives, and thus reduce their joint effectiveness to that of the single person directing them from the centre.
+It would, in effect, paralyse their co-operation." His argument regarding science can be extended to scholarship in general.
+[^n]: See the Routledge Dictionary of Economics entry on "Dutch books."

### 2017-05-25 Draft/draft2.tex
Major update to draft2.Rmd

@@
 
-In this essay I follow the lead of \citet{Coase1974}, and examine the
-very common differential treatment of the market for goods and the
-market for ideas.
+The pursuit of knowledge through academic scholarship rests on a
+commonly held moral foundation. The pursuit of truth, which is widely
+believed to be the goal of scholarship, is thought to be an inherently
+moral activity. At the same time, it is an increasingly widely held
+belief that financial market arbitrage, the kind pursued by Wall Street
+traders, is an inherently immoral activity. Take for example, the case
+of the quantitative proprietary trading firm which serves no clients and
+which invests only the capital of its principals. Such a firm makes its
+profits, often astonishingly large profits, by buying and selling
+financial securities and profiting from speculation. A common line of
+reasoning is that such a firm is predatory, parasitic, and even
+rapacious and as such cannot possibly be acting morally.
 
-The plan of this paper is as follows: section 2 introduces Coases's
-original argument, and his conclusion that their different treatment is
-incongruous; section 3 discusses the view in \citet{Hayek1945} that the
-essential nature of the economic problem is one of the utilization of
-knowledge. For Hayek, the economic process is an information process and
-markets can be seen, using the modern parlance, as information systems.
-There is thus no justification for the differential treatment of goods
-and ideas; section 4 introduces the concept of subjective probability
-following \citet{deFinetti1937}, as well as the Arbitrage Choice Theory
-outlined in \citet{Nau1999}; section 5 explains, as essential
-background, the Dutch Book Theorem; section 6 gives a few chosen
-examples of scholarly debates framed as Dutch Book arguments; section 6
-frames Coases's original argument as a Dutch Book argument; section 7
-concludes.
+In this paper, I argue that one cannot simultaneously hold the above two
+positions without behaving incoherently. The process of scholarship and
+financial trading are both examples of finding and exploiting Dutch
+books. Dutch books are simply arbitrage by another name. Thus
+scholarship can be seen, indeed is most properly seen, as a form of
+intellectual arbitrage. Just as traders find mispricings in financial
+securities and exploit them for financial profit, scholars find
+misunderstandings - mispricings by another name - and exploit them to
+establish their scholarly reputation.
+
+The paper is organized as follows. I outline an original discussion due
+to \citet{Coase1974} of the ``market for ideas'' and the ``market for
+goods,'' and discuss his conclusion that their different treatment is
+incongruous in Section 2. I then discuss the idea, due to
+\citet{Hayek1945}, that the economic process is an information process
+in its most essential treatment in Section 3. In Section 4 I outline the
+concept of subjective probability following \citet{deFinetti1937}, as
+well as Arbitrage Choice Theory put forward by \citet{Nau1999}. In
+Section 5 I explain the Dutch Book Theorem as essential background to my
+argument. I give a few chosen examples of scholarly debates framed as
+Dutch Book arguments in Section 6. In Section 7 I present my own Dutch
+book argument. Section 8 concludes the paper.
 
@@
 
-\section{The Use of Knowledge in
-Society}\label{the-use-of-knowledge-in-society}
+\citet{Coase1974} points out that there has been a common tradition of
+drawing a sharp distinction between the ``market for goods'' and the
+``market for ideas.'' The ``market for ideas'' is the domain of
+intellectuals and consists of speech, writing, and religious belief -
+activities covered by the First Amendment. Coase notes that the common
+view has been that the ``market for goods'' requires extensive
+regulation to promote public interest, while the ``market for ideas''
+would be greatly harmed by such regulatory activity. He writes ``the
+Western world, by and large, accepts the distinction and the policy
+recommendations that go with it.'' For Coase, such an attitude is
+unjustified.
+
+Coase writes that ``\ldots{} belief in a free market in ideas does not
+have the same roots as belief in the value of free trade in goods.'' And
+further that, ``\ldots{} this view of the peculiar status of the market
+for ideas has been nourished by a commitment to democracy as exemplified
+in the political institutions of the United States, for whose efficient
+working a market in ideas not subject to government regulation is
+considered essential.'' Speaking of intellectuals Coase highlights that
+``intellectuals have shown a tendency to exalt the market for ideas and
+to depreciate the market for goods.'' But why should this differential
+treatment be so? For Coase the distinction is invalid as ``{[}t{]}here
+is no fundamental difference between these two markets.'' He goes on to
+argue that we should use the same approach for all markets when deciding
+upon public policy.
+
+For Coase the explanation for the tendency on the part of intellectuals
+to make a sharp distinction between the two markets is self-interest and
+self-esteem. In offering this explanation, he echoes the Public Choice
+literature: self-interest leads intellectuals to see themselves as the
+experts who will plan and implement the regulation of the market for
+goods, while self-esteem causes them to deny any role for regulation of
+their domain - the market for ideas. Coase urges intellectuals to
+``\ldots{} adopt a more consistent view.''\footnote{For a book-length
+  treatment of such tendencies on the part of intellectuals see
+  \citet{Sowell2009}.} Expressing his dismay at this situation he
+writes:
+
+\begin{quote}
+It is hard to believe that the general public is in a better position to
+evaluate competing views on economic and social policy than to choose
+between different kinds of food.
+\end{quote}
+
+Indeed, this is puzzling, as is the distinction between the ethical
+underpinnings of the two markets. The discussion in \citet{Coase1974} is
+helpful in framing the current discussion. Most essential is the
+perspective that intellectuals operate within a market setting when
+producing and promoting their ideas.\footnote{Elsewhere
+  \citet{Polanyi2000} has made a similar case.} The sharp distinction
+between the two markets when it comes to the role of government
+regulation parallels the common sharp distinction of their respective
+moral nature. When the scholar operates in the ``market for ideas'' it
+is commonly believed that her efforts are inherently ethical, resting on
+a long history and strong tradition of common moral values. While it is
+often the case, especially among intellectuals, to depreciate the moral
+value of capitalist enterprise that is the domain of the financial
+trader. Echoing Coase I argue below that this practice is unfounded, and
+I urge the adoption of a more consistent view as there is no fundamental
+difference between the two activities. They are both examples of
+arbitrage within their respective domains.
+
+\section{The Informational Role of
+Prices}\label{the-informational-role-of-prices}
+
+Once the domain of intellectuals is seen as a market - the ``market for
+ideas'' - we can inquire about the special nature of markets to better
+understand their ethical foundation. The essential element is that
+competitive markets are mediated by prices, and prices serve as signals
+of information. As \citet{Grossman1989} writes ``{[}i{]}t is a common
+theme of most discussions of the competitive price system that prices
+convey information.''\footnote{See also \citet{Kreps1988} who states
+  that ``the notion that prices contain and convey information is
+  standard doctrine among economists.''} This concept in its original
+formulation is due to \citet{Hayek1945}, who wrote
+
+\begin{quote}
+\textbf{\emph{We must look at the price system as \ldots{} a mechanism
+for communicating information if we want to understand its real
+function}}\ldots{} The most significant fact about this system is the
+economy of knowledge with which it operates, or how little the
+individual participants need to know in order to be able to take the
+right action \ldots{} by a kind of symbol, only the most essential
+information is passed on\ldots{}"
+\end{quote}
+
+For Hayek, the essential element of markets is that they are information
+systems, as we might say in the modern parlance.\footnote{Hayek wrote:
+  ``It is more than a metaphor to describe the price system as a kind of
+  machinery for registering change, or a \emph{system of
+  telecommunications}.'' Emphasis added.} Hayek wrote in the midst of
+the so-called socialist calculation debate. The Polish economist Oskar
+Lange (see \citet{Lange1936} and \citet{Lange1937}) argued that taking
+mathematical models of neoclassical economics seriously, the competitive
+allocation of the market could be replicated by a central planner making
+socialism a viable economic system. Hayek vehemently opposed this view
+highlighting that the would-be central planner faces an insurmountable
+knowledge problem because the knowledge that must be made use of for
+such planning is dispersed widely among many people, who each possess
+only an incomplete and partial knowledge.\footnote{\citet{Polanyi2000}
+  makes a similar argument regarding a knowledge problem in science. He
+  writes: ``Any attempt to organize the group \ldots{} under a single
+  authority would eliminate their independent initiatives, and thus
+  reduce their joint effectiveness to that of the single person
+  directing them from the centre. It would, in effect, paralyse their
+  co-operation.'' His argument regarding science can be extended to
+  scholarship in general.}
+
+Similar to Coase, Hayek points out the tendency of some to make a sharp
+distinction between different kinds of knowledge. He writes ``one kind
+of knowledge, namely, scientific knowledge, occupies now so prominent a
+place in public imagination that we tend to forget that it is not the
+only kind that is relevant.'' Indeed, by taking advantage of relative
+mispricings among commodities the financial trader benefits his fellow
+men by allocating resources more efficiently. But this is hardly viewed
+as a noble act, not nearly so noble as scientific discovery or academic
+expression. Hayek saw keenly the situation:
+
+\begin{quote}
+It is a curious fact that this sort of knowledge should today be
+generally regarded with a kind of contempt, and that someone who by such
+knowledge gains an advantage over somebody better equipped with
+theoretical or technical knowledge is thought to have acted almost
+disreputably. To gain advantage from better knowledge of facilities of
+communication or transport is sometimes regarded as almost dishonest,
+although it is quite as important that society make use of the best
+opportunities in this respect as in using the latest scientific
+discoveries.
+\end{quote}
+
+The lesson regarding the relative importance of different kinds of
+knowledge that Hayek teaches is a very deep one. Indeed, when this
+insight is fully appreciated one begins to see that the use of mundane
+kinds of knowledge - Hayek's ``knowledge of time and place'' is
+essential. It is not exaggeration to state that if the only knowledge
+that society could usefully exploit was that from universities, the
+press, literature and science we would all starve to death in very short
+order. The financial arbitrageur is a perfect example of Hayek's ``man
+on the spot'' and his actions benefit his fellows greatly. Still, when
+one thinks of the abstract concept of the pursuit of knowledge, images
+of the scientist in the lab or of the scholar in the library come more
+easily to mind than the trader scanning prices on his bank of monitors.
+But for Hayek:
+
+\begin{quote}
+the \emph{arbitrageur} who gains from local differences of commodity
+prices, {[}is{]} performing {[}an{]} eminently useful function based on
+special knowledge of circumstances of the fleeting moment not known to
+others.
+\end{quote}
+
+The actions of the arbitrageur are indeed eminently useful! Consider the
+commodities that we require in our daily lives such as sugar, coffee,
+wheat, milk, and oil that come to us more efficiently and at lower cost
+than would otherwise be the case if not for the actions of commodity
+traders. In addition, because of financial traders retirement is secured
+more soundly through investment. And risks are insured against,
+eliminated and transferred through financial markets that we would
+otherwise have to bear.
+
+Hayek compared the price system to ``a kind of machinery for registering
+change'' and as a ``system of telecommunications.'' Similarly,
+\citet{Scarf1990} has made an analogy between the market institution and
+a massively distributed analog computer that computes values in the form
+of prices. Following this line of reasoning, all market processes are
+knowledge processes. Therefore there is no sharp distinction between the
+``market for ideas'' and the ``market for goods'', as Coase referred to
+them. They are simply both markets and differ only in their relative
+kinds of knowledge. \citet{Sowell1996} has made this point quite
+succinctly:
+
+\begin{quote}
+While market economies are often thought of as money economies, they are
+still more so knowledge economies\ldots{} Economic transactions are
+purchases and sales of knowledge.
+\end{quote}
+
+\begin{quote}
+After all, the cavemen had the same natural resources at their disposal
+as we have today\ldots{} We are all in the business of buying and
+selling knowledge from one another, because we are each so profoundly
+ignorant of what it takes to complete the whole process of which we are
+part.
+\end{quote}
+
+My argument, echoing Coase and augmented by a sound understanding of
+market processes as information processes from Hayek, is that we should
+adopt a more coherent view of the ethical and moral foundations of both
+markets, for they are fundamentally of the same nature.
 
@@
 
-\section{The Dutch Book Theorem
+The link between the market for ideas and the market for goods is
+further strengthened by considering the work of the decision theorist
+Robert Nau. For example, \citet{NauMcCardle1991} state that the
+principle of no-arbitrage, which is fundamental in finance theory, is
+the common foundation of decision theory, game theory and competitive
+market theory. \citet{Nau1999} refers to this as Arbitrage Choice
+Theory, following the Bayesian Dutch book arguments of
+\citet{deFinetti1937}. A Dutch book is a situation in which an
+individual holds incoherent beliefs (beliefs inconsistent with the basic
+axioms of probability), and if forced to bet on them exposes themselves
+to a guaranteed loss. When market transactions are seen as knowledge
+transactions, it becomes clear that a Dutch book is equivalent to
+arbitrage - the good old fashioned kind often derided from the world of
+finance.
+
+When a trader makes a profit by simultaneously buying and selling
+financial securities to exploit relative mispricings, this arbitrage is
+simply the exploitation of a Dutch book expressed as incoherent market
+prices. Likewise the intellectual pursuit of knowledge, what Coase
+called the ``market for ideas'' can be seen as the pursuit of arbitrage,
+or Dutch books, in the existing body of academic knowledge. Consider a
+young scholar who discovers an error in the received theory of their
+specific academic domain, and who makes a name for themselves by
+publishing an article correcting the error in a reputable academic
+journal. This can now be easily understood to be the exploitation of a
+Dutch book, or intellectual arbitrage.
+
+\subsection{The Dutch Book Theorem
 Explained}\label{the-dutch-book-theorem-explained}
+
+Coherence in de Finetti's definition of probability is the counterpart
+of the modern theory of no-arbitrage in finance.\footnote{See
+  \citet{PressaccoZiani2010}.} Interestingly, de Finetti took a very
+operational and economic approach to eliciting subjective probabilities.
+
+The axioms of probability which characterize any theory of probability
+arise logically from the condition that subjective probabilities
+function as prices obeying coherency (i.e.~the arbitrage free
+conditions).
+
+Looking at problems of uncertainty as situations in which various
+contingent claims are traded is the key insight offered by the
+state-preference theory.
 
@@
 
+The following example serves to demonstrate the principle. Consider
+agent A's degree of belief regarding the flipping of a fair coin. The
+event space is represented by \(S = \{H, T\}\) where \(H\) represents
+`heads' and \(T\) represents `tails.' Suppose A's degrees of belief are
+expressed as probabilities:
+\(P(H) = 0.51 \quad \mbox{and} \quad P(T) = 0.51\). That is, A is
+willing to pay \(\$0.51\) to receive \(\$1\) in the event of a `heads',
+and also \(\$0.51\) to receive \(\$1\) in the event of a `tails.' It is
+easy to see that A is acting incoherently. The book maker will be
+willing to take both bets simultaneously. Either `heads' or a `tails'
+will occur, so if A offers both bets simultaneously she will be
+guaranteed to earn \(\$1\). But the total of her bets is \(\$1.02\), so
+net of her bets she will lose \(\$0.02\) whatever the state of the
+world. A Dutch book has been made against her.
+
+In the nomenclature of finance a Dutch book is an arbitrage and the
+person making a Dutch book against an opponent is called an arbitrageur.
+For de Finetti the bookmaker whose gain is certain in a given bet is no
+different than the trader who earns a guaranteed profit by buying low
+and selling high when an asset is mispriced.
+
+For de Finetti probabilities are prices. In modern finance theory prices
+are probabilities. In the end it is an equivalence.
+
+Once seen through the lens of subjective probability, it becomes clear
+that what applies to mispriced assets also applies to misplaced
+probabilities. They are both examples of incoherent beliefs.
+
 \subsection{Examples of Dutch Book
@@
 
-\section{Coase's Dutch Book Argument}\label{coases-dutch-book-argument}
+\begin{itemize}
+\item
+  Culp \& Miller vs.~Pirrong re: whether or not MG was a prudent hedger
+\item
+  Swinburne vs.~Howson re: whether or not God exists
+\item
+  The morality of scholarship vs the morality of arbitrage is an example
+  of a DBA.
+\end{itemize}
+
+\section{The Dutch Book Argument}\label{the-dutch-book-argument}
 

### 2017-05-25 Draft/morality-of-arbitrage.Rmd
Final submission to Mercatus.

--- 2017-05-25 Draft/draft2.Rmd
@@
 ---
+title: "The Morality of Arbitrage"
+author:
+- affiliation: Utah State University
+  name: Tyler J. Brough
+date: "May 25, 2017"
 output:
@@
     citation_package: natbib
-    keep_tex: true
-    fig_caption: true
+    fig_caption: yes
+    keep_tex: yes
     latex_engine: pdflatex
     template: ./svm-latex-ms.tex
-title: "The Morality of Arbitrage"
-author:
-- name: Tyler J. Brough
-  affiliation: Utah State University
-abstract: "In this paper, I argue that one cannot rationally believe that financial arbitrage is an inherently immoral pursuit, while simultaneously believing that the pursuit of academic knowledge is an inherently moral pursuit.
-I argue that these two seemingly separate activities are really one and the same.
-Further those that do hold such contradictory beliefs are behaving incoherently and have a Dutch book made against them."
-keywords: "arbitrage, Dutch books, morality"
-date: "`r format(Sys.time(), '%B %d, %Y')`"
-geometry: margin=1in
+  html_document: default
+  word_document: default
+biblio-style: apsr
 fontfamily: mathpazo
 fontsize: 11pt
+geometry: margin=1in
+keywords: arbitrage, Dutch books, morality
+bibliography: ./master.bib
 spacing: double
-bibliography: ./master.bib
-biblio-style: apsr
+abstract: In this paper, I argue that one cannot rationally believe that financial
+  arbitrage is an inherently immoral pursuit, while simultaneously believing that
+  the pursuit of academic knowledge is an inherently moral pursuit. I argue that these
+  two seemingly separate activities are really one and the same. Further those that
+  do hold such contradictory beliefs are behaving incoherently and have a Dutch book
+  made against them.
 ---
@@
 I then discuss the idea, due to @Hayek1945, that the economic process is an information process in its most essential treatment in Section 3.
-In Section 4 I outline the concept of subjective probability following @deFinetti1937, as well as Arbitrage Choice Theory put forward by @Nau1999.
+In Section 4 I outline the concept of subjective probability following @deFinetti1937, as well as arbitrage choice theory put forward by @Nau1999.
 In Section 5 I explain the Dutch Book Theorem as essential background to my argument.
@@
 no-arbitage is the core principle of rationality which remains after economic models are stripped of their excess baggage of intrinsically unverifiable or empirically disconfirmed assumptions..." The arbitrageur is Hayek's "man on the spot" who provides a useful informational service by correcting incoherent price signals.
-This is true in commodities and financial assets as well as in
+This is as true for commodities and financial assets as well as for scholarly articles, bestsellers, speeches, and conference presentations.
 
@@
 
-Coherence in de Finetti's definition of probability is the counterpart of the modern theory of no-arbitrage in finance.[^5] Interestingly, de Finetti took a very operational and economic approach to eliciting subjective probabilities.
+For de Finetti probability represents the subjective beliefs of the agent.
+As @Nau2001 explains: "probability does not exist *objectively*, independently of the human mind.
+[P]robability ...
+is a rate at which an individual is willing to *bet on* the occurence of an event.
+Betting rates are the primitive measurements that reveal *your* probabilities or *someone else's* probabilities, which are the only probabilities that really exist." de Finetti took a very operational view of eliciting probabilities.
+In his theory, "bets are for money, so your probability of an event is effectively the *price* that you are willing to pay for a lottery ticket that yields $1$ unit of money if the event occurs and nothing otherwise." The reader trained in economics or finance will notice the connection to the state-price theory of decision making under uncertainty of @Arrow1964 and @Debreu1959.[^y] Coherence in de Finetti's definition of probability is the counterpart of the modern theory of no-arbitrage in finance.[^5]
 
-The axioms of probability which characterize any theory of probability arise logically from the
+The axioms of probability which characterize any valid theory of probability arise logically from the
 condition that subjective probabilities function as prices obeying coherency (i.e. the arbitrage free
 conditions).
+Looking at problems of uncertainty as situations in which various contingent claims are traded is the key insight offered by the state-preference theory.
+ACT differs from the Arrow-Debreu setting in that probabilities and utilities are non-separable, and only de Finetti's *previsions* are observable.
+In the modern parlance of financial economics these are *risk-neutral probabilities* (the product of state-dependent subjective probabilities and utilities).
+ACT relaxes the stance of methogological individualism of the neoclassical trading.
+Rationality characterizes a market-level phenomenon rather than individual behavior.
+Agents learn to be rational by adopting the market's risk-neutral density as their prior through the market exchange process.
+The connection to the information process in the Hayekian setting becomes clear: prices convey information and represent agents' subjective beliefs.
 
-Looking at problems of uncertainty as situations in which various contingent claims are traded is the key insight offered by the state-preference theory.
-
-The dictionary definition of a Dutch book is the following:
+With this discussion of subjective probability and ACT as background we can now discuss the Dutch Book Theorem. The dictionary definition of a Dutch book is the following:
 
@@
 That is, A is willing to pay $\$0.51$ to receive $\$1$ in the event of a 'heads', and also $\$0.51$ to receive $\$1$ in the event of a 'tails.' It is easy to see that A is acting incoherently.
-The book maker will be willing to take both bets simultaneously.
+The bookmaker will be willing to take both bets simultaneously.
 Either 'heads' or a 'tails' will occur, so if A offers both bets simultaneously she will be guaranteed to earn $\$1$.
@@
 For de Finetti the bookmaker whose gain is certain in a given bet is no different than the trader who earns a guaranteed profit by buying low and selling high when an asset is mispriced.
+Once seen through the lens of subjective probability, it becomes clear that what applies to mispriced assets also applies to misplaced probabilities.
+They are both examples of incoherent beliefs.
 
-For de Finetti probabilities are prices. In modern finance theory prices are probabilities. In the end it is an equivalence.
+According to The Cambridge Dictionary of Philosophy (see @CambDictPhil), the Dutch book theorem can be stated as follows:
 
-Once seen through the lens of subjective probability, it becomes clear that what applies to mispriced assets also applies to misplaced probabilities. They are both examples of incoherent beliefs.
+> The proposition that anyone who (a) counts a bet on a proposition p as fair if the odds correspond to his degree of belief that p is true and who (b) is willing to make any combinations of bets he would regard individually as fair will be vulnerable to a Dutch book provided his degrees of belief do not conform to the axioms of of the probability calculus.
+Thus, anyone of whom (a) and (b) are true and whose degree of belief in a disjunction of two incompatible propositions is not equal to the sum of his degrees of belief in the two propositions taken individually would be vulnerable to a Dutch book.
 
-## Examples of Dutch Book Arguments
+Through the price mechanism and the process of exchange agents's beliefs become coherent as people learn to avoid arbitrage.
+Again, this is true for security markets and for scholarship.
+The same market process of *tatonnement* operates in the market for goods and in the market for ideas.
+Market processes are information processes!
 
-- Culp & Miller vs. Pirrong re: whether or not MG was a prudent hedger
-- Swinburne vs. Howson re: whether or not God exists
-
-- The morality of scholarship vs the morality of arbitrage is an example of a DBA.
+The pursuit of truth that is held as inherently moral in the market for ideas is the same information dynamic that underlies financial and commodity trading.
+The difference is the relative kinds of knowledge that are processed in the respective markets.
+While the kinds of knowledge being processed in securities and commodities is more mundane, as Hayek wrote it is no less essential to an efficient, orderly, and rational economic order.
 
@@
 
-# Conclusion
+I can now state the main argument of the paper.
+Given that the "market for goods" and the "market for ideas" are both examples of the same underlying information process: One cannot simultaneously belief that (a) the pursuit of knowledge in scholarship (intellectual arbitrage) is inherently moral, and that (b) the pursuit of trading profits in securities markets (financial arbitrage) is inherently immoral without becoming vulnerable to a Dutch book.
+
+The "market for goods" and the "market for ideas" share a common moral foundation. The same criteria that we use to evaluate one should apply equally to the other.
 
@@
 It would, in effect, paralyse their co-operation." His argument regarding science can be extended to scholarship in general.
+[^y]: For a helpful review of state preference theory see Chapter 4 of @CopelandWestonShastri.
 [^n]: See the Routledge Dictionary of Economics entry on "Dutch books."

### 2017-05-25 Draft/morality-of-arbitrage.tex
Final submission to Mercatus.

--- 2017-05-25 Draft/draft2.tex
@@
 concept of subjective probability following \citet{deFinetti1937}, as
-well as Arbitrage Choice Theory put forward by \citet{Nau1999}. In
+well as arbitrage choice theory put forward by \citet{Nau1999}. In
 Section 5 I explain the Dutch Book Theorem as essential background to my
@@
 the common foundation of decision theory, game theory and competitive
-market theory. \citet{Nau1999} refers to this as Arbitrage Choice
-Theory, following the Bayesian Dutch book arguments of
+market theory. \citet{Nau1999} refers to this as \emph{arbitrage choice
+theory} (ACT), following the Bayesian Dutch book arguments of
 \citet{deFinetti1937}. A Dutch book is a situation in which an
@@
 arbitrage - the good old fashioned kind often derided from the world of
-finance.
+finance. In ACT ``\ldots{} no-arbitage is the core principle of
+rationality which remains after economic models are stripped of their
+excess baggage of intrinsically unverifiable or empirically disconfirmed
+assumptions\ldots{}'' The arbitrageur is Hayek's ``man on the spot'' who
+provides a useful informational service by correcting incoherent price
+signals. This is as true for commodities and financial assets as well as
+for scholarly articles, bestsellers, speeches, and conference
+presentations.
 
@@
 
-Coherence in de Finetti's definition of probability is the counterpart
-of the modern theory of no-arbitrage in finance.\footnote{See
-  \citet{PressaccoZiani2010}.} Interestingly, de Finetti took a very
-operational and economic approach to eliciting subjective probabilities.
+For de Finetti probability represents the subjective beliefs of the
+agent. As \citet{Nau2001} explains: ``probability does not exist
+\emph{objectively}, independently of the human mind. {[}P{]}robability
+\ldots{} is a rate at which an individual is willing to \emph{bet on}
+the occurence of an event. Betting rates are the primitive measurements
+that reveal \emph{your} probabilities or \emph{someone else's}
+probabilities, which are the only probabilities that really exist.'' de
+Finetti took a very operational view of eliciting probabilities. In his
+theory, ``bets are for money, so your probability of an event is
+effectively the \emph{price} that you are willing to pay for a lottery
+ticket that yields \(1\) unit of money if the event occurs and nothing
+otherwise.'' The reader trained in economics or finance will notice the
+connection to the state-price theory of decision making under
+uncertainty of \citet{Arrow1964} and \citet{Debreu1959}.\footnote{For a
+  helpful review of state preference theory see Chapter 4 of
+  \citet{CopelandWestonShastri}.} Coherence in de Finetti's definition
+of probability is the counterpart of the modern theory of no-arbitrage
+in finance.\footnote{See \citet{PressaccoZiani2010}.}
 
-The axioms of probability which characterize any theory of probability
-arise logically from the condition that subjective probabilities
-function as prices obeying coherency (i.e.~the arbitrage free
-conditions).
+The axioms of probability which characterize any valid theory of
+probability arise logically from the condition that subjective
+probabilities function as prices obeying coherency (i.e.~the arbitrage
+free conditions). Looking at problems of uncertainty as situations in
+which various contingent claims are traded is the key insight offered by
+the state-preference theory. ACT differs from the Arrow-Debreu setting
+in that probabilities and utilities are non-separable, and only de
+Finetti's \emph{previsions} are observable. In the modern parlance of
+financial economics these are \emph{risk-neutral probabilities} (the
+product of state-dependent subjective probabilities and utilities). ACT
+relaxes the stance of methogological individualism of the neoclassical
+trading. Rationality characterizes a market-level phenomenon rather than
+individual behavior. Agents learn to be rational by adopting the
+market's risk-neutral density as their prior through the market exchange
+process. The connection to the information process in the Hayekian
+setting becomes clear: prices convey information and represent agents'
+subjective beliefs.
 
-Looking at problems of uncertainty as situations in which various
-contingent claims are traded is the key insight offered by the
-state-preference theory.
-
-The dictionary definition of a Dutch book is the following:
+With this discussion of subjective probability and ACT as background we
+can now discuss the Dutch Book Theorem. The dictionary definition of a
+Dutch book is the following:
 
@@
 and also \(\$0.51\) to receive \(\$1\) in the event of a `tails.' It is
-easy to see that A is acting incoherently. The book maker will be
-willing to take both bets simultaneously. Either `heads' or a `tails'
-will occur, so if A offers both bets simultaneously she will be
-guaranteed to earn \(\$1\). But the total of her bets is \(\$1.02\), so
-net of her bets she will lose \(\$0.02\) whatever the state of the
-world. A Dutch book has been made against her.
+easy to see that A is acting incoherently. The bookmaker will be willing
+to take both bets simultaneously. Either `heads' or a `tails' will
+occur, so if A offers both bets simultaneously she will be guaranteed to
+earn \(\$1\). But the total of her bets is \(\$1.02\), so net of her
+bets she will lose \(\$0.02\) whatever the state of the world. A Dutch
+book has been made against her.
 
@@
 different than the trader who earns a guaranteed profit by buying low
-and selling high when an asset is mispriced.
+and selling high when an asset is mispriced. Once seen through the lens
+of subjective probability, it becomes clear that what applies to
+mispriced assets also applies to misplaced probabilities. They are both
+examples of incoherent beliefs.
 
-For de Finetti probabilities are prices. In modern finance theory prices
-are probabilities. In the end it is an equivalence.
+According to The Cambridge Dictionary of Philosophy (see
+\citet{CambDictPhil}), the Dutch book theorem can be stated as follows:
 
-Once seen through the lens of subjective probability, it becomes clear
-that what applies to mispriced assets also applies to misplaced
-probabilities. They are both examples of incoherent beliefs.
+\begin{quote}
+The proposition that anyone who (a) counts a bet on a proposition p as
+fair if the odds correspond to his degree of belief that p is true and
+who (b) is willing to make any combinations of bets he would regard
+individually as fair will be vulnerable to a Dutch book provided his
+degrees of belief do not conform to the axioms of of the probability
+calculus. Thus, anyone of whom (a) and (b) are true and whose degree of
+belief in a disjunction of two incompatible propositions is not equal to
+the sum of his degrees of belief in the two propositions taken
+individually would be vulnerable to a Dutch book.
+\end{quote}
 
-\subsection{Examples of Dutch Book
-Arguments}\label{examples-of-dutch-book-arguments}
+Through the price mechanism and the process of exchange agents's beliefs
+become coherent as people learn to avoid arbitrage. Again, this is true
+for security markets and for scholarship. The same market process of
+\emph{tatonnement} operates in the market for goods and in the market
+for ideas. Market processes are information processes!
 
-\begin{itemize}
-\item
-  Culp \& Miller vs.~Pirrong re: whether or not MG was a prudent hedger
-\item
-  Swinburne vs.~Howson re: whether or not God exists
-\item
-  The morality of scholarship vs the morality of arbitrage is an example
-  of a DBA.
-\end{itemize}
+The pursuit of truth that is held as inherently moral in the market for
+ideas is the same information dynamic that underlies financial and
+commodity trading. The difference is the relative kinds of knowledge
+that are processed in the respective markets. While the kinds of
+knowledge being processed in securities and commodities is more mundane,
+as Hayek wrote it is no less essential to an efficient, orderly, and
+rational economic order.
 
@@
 
-\section{Conclusion}\label{conclusion}
+I can now state the main argument of the paper. Given that the ``market
+for goods'' and the ``market for ideas'' are both examples of the same
+underlying information process: One cannot simultaneously belief that
+(a) the pursuit of knowledge in scholarship (intellectual arbitrage) is
+inherently moral, and that (b) the pursuit of trading profits in
+securities markets (financial arbitrage) is inherently immoral without
+becoming vulnerable to a Dutch book.
+
+The ``market for goods'' and the ``market for ideas'' share a common
+moral foundation. The same criteria that we use to evaluate one should
+apply equally to the other.
 

### 2017-05-25 APEE/render.R

@@ -1,0 +1,2 @@
+library(rmarkdown)
+render("morality-of-arbitrage-abstract.Rmd")

### 2017-06-15 Slides/apee-slides.Rmd
Changes for the APEE presentation.

--- 2016-09-16 Slides/morality-slides.Rmd
@@
 title: "The Morality of Arbitrage"
-author: "Tyler J. Brough"
-date: "September 16, 2016"
-output: ioslides_presentation
+author: "Tyler J. Brough, Ph.D."
+date: "April 11, 2017"
+output: slidy_presentation
 ---
 
-#
+# Introduction
+
+##
 
@@
 
+<div class="notes">
+- Of course, all good ideas begin with Hayek!
+</div>
+
+## About Me
+
+- Financial Economist at Utah State University
+- My research focuses on market microstructure, derivatives markets, financial econometrics, and computational methods.
+- I'm on the [web](https://broughtj.github.io/)
+
+<br>
+
+<center>
+<img src="images/buddy.jpg" width=400 height=350 />
+</center>
+
+## What's Wrong with Capitalism?!
+
+>- It is apparent to me that the standard ethical arguments for capitalism are not having any purchase in the minds of most people.
+>- Capitalism is presented as some kind of Faustian bargain: we like it for its wealth production and efficiency, but at bottom it is really about greed. It is rapacious and immoral.
+>- It is readily apparent that many of our colleagues in the business disciplines believe this notion
+>- __I'm afraid that our students do too!__ They leave the business school with some good technical tools, but not with an appreciation of just how much good they will do in their careers. 
+>- That is on us! That's a failure on our part to teach correct principles.
+
+## Some Recent Anecdotal Evidence
+
+>- The Rolling Stone writes about the [great vampire squid wrapped around the face of humanity](http://www.rollingstone.com/politics/news/the-great-american-bubble-machine-20100405)
+
+<center>
+<img src="images/squid.jpg" width=400 height=350 />
+</center>
+
+## Sadly, Yet More
+
+>- "Derivatives are financial weapons of mass destruction" - Warren Buffett
+>- "Derivatives are toxic - stay away from them" - unnamed donor to the Huntsman School
+>- "In a world where profit is consistently put before both people and the planet, climate economics has everything to do with ethics and morality" - Naomi Klein
+>- CNN asks: [Is democratic socialism the right path for America?](http://www.cnn.com/2015/10/27/opinions/opinion-roundup-socialism/)
+
 ## Introduction
 
->- I have been very influenced by Coases's 1975 AER article *The Market for Goods and the Market for Ideas*.
->- I have also been reading articles lately by Robert Nau and his coauthors. In particular the paper by Nau & McCardle (1991) *Aribtrage, Rationality, and Equilibrium*. 
->- This project is an attempt to do something like what Coase had in mind, using the the approach of Nau, but applied to the morality of markets and capitalism.
+The origins of this project have been slowly baking for some time now:
+
+- I have been very influenced by coase's 1974 AER article [*The Market for Goods and the Market for Ideas*](http://www.jstor.org/stable/1816070?seq=1#page_scan_tab_contents).
+
+- I can date my adult thinking about markets and the market process to my first reading of Hayek's 1945 AER article [*The Use of Knowledge in Society*](http://www.jstor.org/stable/1809376?seq=1#page_scan_tab_contents)
+
+## Coase's Dutch Book Argument
+
+Coase's paper is about what he calls the "economics of the First Ammendment"
+
+For those needing a refresher:
+
+> *"Congress shall make no law respecting an establishment of religion, or prohibiting the free exercise thereof; or abridging the freedom of speech, or of the press; or the right of the people peaceably to assemble, and to petition the Government for a redress of grievances"*
+
+The freedom of speech, a free press, religious liberty are so ingrained in our culture. Their morality is based on a generally held and accepted ethical foundation.
+
+<div class="notes">
+
+If you don't know what a Dutch book is, hang on and I'll explain it.
+</div>
+
+## Coase's Dutch Book Continued
+
+The main idea that he examines:
+
+> *"What is the general view that I will be examining?
+It is that, in the market for goods, government regulation is desirable whereas, in the market for ideas, government regulation is undersirable and should be strictly limited."*
+
+The Dutch book is as follows:
+
+> *"The paradox is that government intervention which is so harmful in the one sphere becomes beneficial in the other."*
+
+and
+
+> *"...
+it is usually those who press most strongly for an extension of government regulation in other markets who are most anxious for a vigorous enforcement of the First Amendment prohibitions on government regulation in the market for ideas"*
+
+## Coase Continued
+
+Coase's take:
+
+> "*Because of the view that a free market in ideas is necessary to the maintenance of democratic institutions and , I believe, for other reasons also, intellectuals have shown a tendency to exalt the market for ideas and to depreciate the market for goods.* ***Such an attitude seems to me unjustified.***"
+
+> *"I would put the point more bluntly.
+The market for ideas is the market in which the intellectual conducts his trade.
+The explanation of the paradox is self-interest and self-esteem.
+Self-esteem leads the intellectuals to magnify the importance of their own market.
+That others should be regulated seems natural, particularly as many of the intellectuals see themselves as doing the regulating.
+But self-interest combines with self-esteem to ensure that, while others are regulated, regulation should not apply to them."*
+
+## Yet more Coase
+
+> *"It is hard to believe that the general public is in a better position to evaluate competing views on economic and social policy than to choose between different kinds of food."*
+
+> *"I do not believe that we will be able to form a judgement in which we can have any confidence unless we abandon the present ambivalence about the performance of government in the two markets and adopt a more consistent view."*
+
+>- One might say a more "***coherent***" view
+
+## Buchanan & Hayek Discussion
+
+<iframe width="1280" height="720" src="https://www.youtube.com/embed/kzNpD9DXU2w" frameborder="0" allowfullscreen></iframe>
+
+<div class="notes">
+Go to 1:39 in the video.
+</div>
 
 ## Nau's Arbitrage Choice Theory
+
+Some time ago I came across Robert Nau's work on [*Arbitrage Choice Theory*](https://faculty.fuqua.duke.edu/~rnau/bio/)
+
+<center>
+<img src="images/Nau.jpg" width=400 height=350 />
+</center>
+
+## Bruno de Finetti
+
+To understand Nau, we need to first understand [Bruno de Finetti](https://en.wikipedia.org/wiki/Bruno_de_Finetti)
+
+<center>
+<img src="images/deFinetti.jpg" width=400 height=350 />
+</center>
+
+## de Finetti and Dutch Books
+
+de Finetti had a very operational view of subjective Bayesian probability.
+
+Nau on de Finetti:
+
+> _"In de Finetti's theory, bets are for money, so your probability of an event is effectively the price that you are willing to pay for a lottery ticket that yields 1 unit of money if the event occurs and nothing otherwise."_
+
+>- My finance colleagues will understand de Finetti's lottery tickets as contingent claims.
+>- In fact, de Finetti already invented much of what we think of as modern finance.
+[But no one really knew about it!](https://www.openstarts.units.it/dspace/bitstream/10077/3969/1/Pressacco%20Ziani%20Atti%20Economia%20e%20Incertezza.pdf)
+
+## Dutch Book Arguments
+
+According to *The Cambridge Dictionary of Philosophy* a Dutch book argument is the following:
+
+> *The argument that a rational person's degrees of belief must conform to the axioms of the probability calculus, since otherwise, by the Dutch book theorem, he would be vulnerable to a Dutch book.*
+
+Okay, so what is the Dutch Book Theorem?
+
+> *The proposition that anyone who (a) counts a bet on a proposition p as fair if the odds correspond to his degree of belief that p is true and who (b) is willing to make any combination of bets he would regard individually as fair will be vulnerable to a Dutch book provided his degrees of belief do not conform to the axioms of the probability calculus.
+Thus, anyone of whom (a) and (b) are true and whose degree of belief in a disjunction of two incompatible propositions is not equal to the sum of his degrees of belief in the two propositions taken individually would be vulnerable to a Dutch book.*
+
+## xkcd On Dutch Books
+
+<center>
+<img src="images/xkcd.png" width=600 height=490 />
+</center>
+
+Here is the [link.](https://xkcd.com/1132/)
+
+## Back to Nau
+
+From Nau's excellent paper [__Arbitrage, Rationality, and Equilibirum__](http://link.springer.com/article/10.1007/BF00132993):
+
+> "*In this paper it will be argued that decision theory, game theory, and market theory can be placed on a more secure and parsimonious footing by appeal to the principle of* ***no arbitrage*** *rather than the usual ordering axioms of preferences.
+The arbitrage princile already has a long history: in the literature on Bayesian statistics and decision theory, it was introduced by de Finetti (1937) as a basis for defining subjective probability...
+In the finance literature, the arbitrage principle explicitly underlies the capital structure theorem (Modigliani & Miller 1958), the valuation of cash flows (Ross 1978), and the pricing of assets and options (Black and Scholes 1973, Merton 1973, Ross 1976).
+No-arbitrage is central to classical welfare economics, where it goes by the name of 'Pareto optimality.' *"
+
+## More Nau
+
+> "*It will be shown here that no-arbitrage is the core principle of rationality which remains after economic models are stripped of their excess baggage of intrinsically unverifiable or empirically disconfirmed assumptions about the perfectness of human cognition, particularly the assumption that belief and preference orderings are complete.
+The arbitrage principle still provides support for the most important concepts of equilibrium in games and markets, but with weaker information requirements.
+It is consistent with 'procedural' or 'cognitive' views of rationality (e.g., Simon 1976; Munier 1991) which emphasize that the information-processing capabilities of the individual are finite and tailored to the specific demands of her physical and cultural environment.*"
+
+And my favorite line:
+
+> "*Thus, Bayesians are made, not born.*"
+
+## Thoughts on Nau
+
+>- So the Dutch book, or equivalently the no-arbitrage principle, becomes a unifying theme. 
+>- We can now explicitly make Coase's argument as a Dutch book argument and point out the incoherence.
+
+<div class="notes">
+Some subtle points:
+
+- Nau points out that probabilities and utilities are inseparable, so we must interpret them as risk-neutral probabilities
+- We in finance are very comfortable with that!
+
+There is much deep material here. So much to be done in following up!
+</div>
+
+## From Nau back to Hayek
+
+The foundational paper in economics, is for me, Hayek's 1945 AER [The Use of Knowledge in Society](http://www.econlib.org/library/Essays/hykKnw1.html)
+
+>- Hayek points out that market processes are knowledge processes, and that markets are information systems to use a modern parlance. 
+>- It should seem very natural to economists to treat the market for ideas and the market for goods similarly. They are two different markets, but the same market process!
+>- Thus, the process of scholarship and science are very much like the market process for goods.
+
+Additionally
+
+>- A successful research project is an intellectual arbitrage.
+>- Students come into our class rooms every day with open Dutch books and pay us to exploit them!
+>- Every technological advance, life-improving result of human ingenuity is entrepreneurial arbitrage!
+
+## Thomas Sowell on Hayek
+
+<center>
+<img src="images/thomas-sowell.jpg" width=600 height=490 />
+</center>
+
+## Thomas Sowell Quotations
+
+> "*While market economies are often thought of as money economies, they are still more so knowledge economies... Economic transactions are purchases and sales of knowledge.*"
+
+> "*After all, the caveman had the same natural resources at their disposal as we have today...
+We are all in the business of buying and selling knowledge from one another, because we are each so profoundly ignorant of what it takes to complete the whole process of which we are a part.*"
+
+## The Morality of Scholarship and the Morality of Arbitrage
+
+>- The process of scholarship is generally accepted as an inherently moral pursuit!
+>- Scholarship, science, and journalism are about important ideas and beliefs.
+>- Economics and finance are about more mundane information processes, but certainly no less vital. Probably much more important to our daily lives!
+
+## Brough's Dutch Book Argument
+
+One cannot simultaneously believe that:
+
+  $(1)$ The pursuit of knowledge (_intellectual arbitrage_) is inherently moral
+
+and that
+
+  $(2)$ The pursuit of capitalist enterprise (_entrepreneurial arbitrage_) is inherently immoral
+
+without leaving oneself open to a massive Dutch book. They are just two different examples of the very same thing!
+
+## Conclusion
+
+>- Thank you for your attention!
+>- Your feedback is appreciated!

### 2017-06-15 Draft/draft2.tex

@@
 
-Coherence in de Finetti's definition of probability is the counterpart
-of the modern theory of no-arbitrage in finance.\footnote{See
-  \citet{PressaccoZiani2010}.} Interestingly, de Finetti took a very
-operational and economic approach to eliciting subjective probabilities.
+For de Finetti probability represents the subjective beliefs of the
+agent. As \citet{Nau2001} explains: ``probability does not exist
+\emph{objectively}, independently of the human mind. {[}P{]}robability
+\ldots{} is a rate at which an individual is willing to \emph{bet on}
+the occurence of an event. Betting rates are the primitive measurements
+that reveal \emph{your} probabilities or \emph{someone else's}
+probabilities, which are the only probabilities that really exist.'' de
+Finettie tool a very operational view of eliciting probabilities. In his
+theory, ``bets are for money, so your probability of an event is
+effectively the \emph{price} that you are willing to pay for a lottery
+ticket that yields \(1\) unit of money if the event occurs and nothing
+otherwise.'' The reader trained in economics or finance will notice the
+connection to the state-price theory of decision making under
+uncertainty of \citet{Arrow1964} and \citet{Debreu1959}.\footnote{For a
+  helpful review of state preference theory see Chapter 4 of
+  \citet{CopelandWestonShastri}.} Coherence in de Finetti's definition
+of probability is the counterpart of the modern theory of no-arbitrage
+in finance.\footnote{See \citet{PressaccoZiani2010}.}
 
-The axioms of probability which characterize any theory of probability
-arise logically from the condition that subjective probabilities
-function as prices obeying coherency (i.e.~the arbitrage free
-conditions).
+The axioms of probability which characterize any valid theory of
+probability arise logically from the condition that subjective
+probabilities function as prices obeying coherency (i.e.~the arbitrage
+free conditions). Looking at problems of uncertainty as situations in
+which various contingent claims are traded is the key insight offered by
+the state-preference theory. ACT differs from the Arrow-Debreu setting
+in that probabilities and utilities are non-separable, and only de
+Finetti's \emph{previsions} are observable. In the modern parlance of
+financial economics these are \emph{risk-neutral probabilities} (the
+product of state-dependent subjective probabilities and utilities). ACT
+relaxes the stance of methogological individualism of the neoclassical
+trading. Rationality characterizes a market-level phenomenon rather than
+individual behavior. Agents learn to be rational by adopting the
+market's risk-neutral density as their prior through the market exchange
+process. The connection to the information process in the Hayekian
+setting becomes clear: prices convey information and represent agents'
+subjective beliefs.
 
-Looking at problems of uncertainty as situations in which various
-contingent claims are traded is the key insight offered by the
-state-preference theory.
-
-The dictionary definition of a Dutch book is the following:
+With this discussion of subjective probability and ACT as background we
+can now discuss the Dutch Book Theorem. The dictionary definition of a
+Dutch book is the following:
 

### 2017-06-23 Slides/morality-slides.Rmd
Changes for the APEE presentation.
Updating with Lewis quotation.

@@
 date: "September 23, 2016"
-output: ioslides_presentation
+output:
+  slidy_presentation: default
+  ioslides_presentation: default
 ---
@@
 
+<br>
+<br>
+
+> *The task of the modern educator is not to cut down jungles but to irriage deserts. The right defense against false
+> sentiments is to inculcate just sentiments. By starving the sensibility of our pupils we only make them easier prey to
+> the propagandist when he comes. For famished nature will be avenged and a hard heart is no infallible protection
+> against a soft head.*
+
+-- C.S. Lewis
+
 <div class="notes">
 - Of course, all good ideas begin with Hayek!
+- And Lewis!
 </div>

### 2017-06-23 Slides/apee-slides.Rmd
Updating slides for Mercatus.

@@
 
-> *But nobody can be a great economist who is only an economist - and I am even tempted to add that the economist who is only an economist is likely to become a nuisance if not a positive danger*.
+> But nobody can be a great economist who is only an economist - and I am even tempted to add that the economist who is only an economist is likely to become a nuisance if not a positive danger.
+>
+>>  -- Friedrich von Hayek
 
--- Friedrich von Hayek
+> The task of the modern educator is not to cut down jungles but to irrigate deserts.
+The right defense against false sentiments is to inculcate just sentiments.
+By starving the sensibility of our pupils we only make them easier prey to the propogandist when he comes.
+For famished nature will be avenged and a hard heart is no infallible protenction against a soft head.
+>
+>>  -- C.S. Lewis
 
@@
 The freedom of speech, a free press, religious liberty are so ingrained in our culture. Their morality is based on a generally held and accepted ethical foundation.
+
+<br>
+You might well ask why there is no ammendment that begins "congress shall make no law regarding the regulation of ..."
 
@@
 
-without leaving oneself open to a massive Dutch book. They are just two different examples of the very same thing!
+without leaving oneself open to a massive Dutch book. They are merely two different examples of the very same thing!
 

### 2017-06-23 Slides/morality-slides.Rmd
Updating slides for Mercatus.

--- 2016-09-23 Slides/morality-slides.Rmd
@@
 date: "September 23, 2016"
-output: ioslides_presentation
+output:
+  slidy_presentation: default
+  ioslides_presentation: default
 ---
 
-#
+##
 
@@
 
--- Friedrich von Hayek
+> -- Friedrich von Hayek
+
+<br>
+<br>
+
+> *The task of the modern educator is not to cut down jungles but to irriage deserts.
+The right defense against false sentiments is to inculcate just sentiments.
+By starving the sensibility of our pupils we only make them easier prey to the propagandist when he comes.
+For famished nature will be avenged and a hard heart is no infallible protection against a soft head.*
+
+> -- C.S. Lewis
 
@@
 - Of course, all good ideas begin with Hayek!
+- And Lewis!
 </div>

### 2017-06-25 Slides/mercatus-slides.Rmd
Updating for Mercatus presentation.

--- 2017-06-23 Slides/apee-slides.Rmd
@@
 
->- It is apparent to me that the standard ethical arguments for capitalism are not having any purchase in the minds of most people.
+>- It is apparent to me that the standard ethical arguments for capitalism are not having much purchase in the minds of most people.
 >- Capitalism is presented as some kind of Faustian bargain: we like it for its wealth production and efficiency, but at bottom it is really about greed. It is rapacious and immoral.
@@
 
+## A Simple Dutch Book Example
+
+- Consider Agent A's degrees of belief regarding the flipping of a fair coin.
+
+- The event space is $S = \{H,T \}$ $\quad \quad$ ($H = \mbox{"heads"}$, and $T = \mbox{"tails"}$)
+
+- Suppose A's beliefs can be represented as $P(H) = 0.51$ and $P(T) = 0.51$
+
+- That is, A will pay $\$0.51$ to receive $\$1$ in the event of a "heads", and simultaneously will pay $\$0.51$ to receive $\$1$ in event of a "tails".
+
+- Now, either a "heads" or "tails" will occur, so A is guaranteed to earn $\$1$ regardless of the state of the world that results
+
+- But A's bets total $\$1.02$, so A is guaranteed to lose $\$0.02$ regardless of the state of the world that results.
+
+- A Dutch book has been made against A!
+
 ## xkcd On Dutch Books
@@
 <center>
-<img src="images/xkcd.png" width=600 height=490 />
+<img src="images/xkcd.png" width=600 height=550 />
 </center>
